### 2020-04-25 paper/ms.tex
simplify and add docker

\documentclass[conference]{IEEEtran}
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{diagbox}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{tikz}
\renewcommand\theadfont{\bfseries}
\IEEEoverridecommandlockouts
\graphicspath{{./images/}}

\begin{document}

\title{\LARGE \bf Signal2Image Modules in Deep Neural Networks for EEG Classification}
\author{Paschalis Bizopoulos, George I. Lambrou and Dimitrios Koutsouris%
\thanks{The authors are with Biomedical Engineering Laboratory, School of Electrical and Computer Engineering, National Technical University of Athens, Athens 15780, Greece e-mail: {\tt\small pbizopoulos@biomed.ntua.gr}, {\tt\small glamprou@med.uoa.gr}, {\tt\small dkoutsou@biomed.ntua.gr.}}
}

\maketitle

\begin{abstract}
	Deep learning has revolutionized computer vision utilizing the increased availability of big data and the power of parallel computational units such as graphical processing units.
	The vast majority of deep learning research is conducted using images as training data, however the biomedical domain is rich in physiological signals that are used for diagnosis and prediction problems.
	It is still an open research question how to best utilize signals to train deep neural networks.

	In this paper we define the term Signal2Image (S2Is) as trainable or non-trainable prefix modules that convert signals, such as Electroencephalography (EEG), to image-like representations making them suitable for training image-based deep neural networks defined as `base models'.
	We compare the accuracy and time performance of four S2Is (`signal as image', spectrogram, one and two layer Convolutional Neural Networks (CNNs)) combined with a set of `base models' (LeNet, AlexNet, VGGnet, ResNet, DenseNet) along with the depth-wise and 1D variations of the latter.
	We also provide empirical evidence that the one layer CNN S2I performs better in eleven out of fifteen tested models than non-trainable S2Is for classifying EEG signals and present visual comparisons of the outputs of some of the S2Is.
\end{abstract}

\section{INTRODUCTION}
Most methods for solving biomedical problems until recently involved handcrafting features and trying to mimic human experts, which is increasingly proven to be inefficient and error-prone.
Deep learning is emerging as a powerful solution for a wide range of problems in biomedicine achieving superior results compared to traditional machine learning.
The main advantage of methods that use deep learning is that they automatically learn hierarchical features from training data making them scalable and generalizable.
This is achieved with the use of multilayer networks, that consist of million parameters~\cite{krizhevsky2012imagenet}, trained with backpropagation~\cite{rumelhart1986learning} on large amount of data.
Although deep learning is mainly used in biomedical images there is also a wide range of physiological signals, such as Electroencephalography (EEG), that are used for diagnosis and prediction problems.
EEG is the measure of the electrical field produced by the brain and is used for sleep pattern classification~\cite{aboalayon2016sleep}, brain computer interfaces~\cite{al2017review}, cognitive/affective monitoring~\cite{lotte1999electroencephalography} and epilepsy identification~\cite{acharya2013automated}.

Yannick et al.~\cite{yannick2019deep} reviewed deep learning studies using EEG and have identified a general increase in accuracy when deep learning and specifically Convolutional Neural Networks (CNNs) are used instead of traditional machine learning methods.
However, they do not mention which specific characteristics of CNN architectures are indicated to increase performance.
It is still an open research question how to best use EEG for training deep learning models.

One common approach that previous studies have used for classifying EEG signals was feature extraction from the frequency and time-frequency domains utilizing the theory behind EEG band frequencies~\cite{langkvist2012sleep}: delta (0.5-4 Hz), theta (4-8 Hz), alpha (8-13 Hz), beta (13-20 Hz) and gamma (20-64 Hz).
Truong et al.~\cite{truong2018convolutional} used Short-Time Fourier Transform (STFT) on a 30 second sliding window to train a three layer CNN on stacked time-frequency representations for seizure prediction and evaluated their method on three EEG databases.
Khan et al.~\cite{khan2018focal} transformed the EEGs in time-frequency domain using multi-scale wavelets and then trained a six layer CNN on these stacked multi-scale representations for predicting the focal onset seizure demonstrating promising results.

Feature extraction from the time-frequency domain has also been used for other EEG related tasks, besides epileptic seizure prediction.
Zhang et al.~\cite{zhang2017pattern} trained an ensemble of CNNs containing two to ten layers using STFT features extracted from EEG band frequencies for mental workload classification.
Giri et al.~\cite{giri2016ischemic} extracted statistical and information measures from frequency domain to train an 1D CNN with two layers to identify ischemic stroke.

For the purposes of this paper and for easier future reference we define the term Signal2Image module (S2I) as any module placed after the raw signal input and before a `base model' which is usually an established architecture for imaging problems.
An important property of a S2I is whether it consists of trainable parameters such as convolutional and linear layers or it is non-trainable such as traditional time-frequency methods.
Using this definition we can also derive that most previous methods for EEG classification use non-trainable S2Is and that no previous study has compared trainable with non-trainable S2Is.

In this paper we compare non-trainable and trainable S2Is combined with well known `base models' neural network architectures along with the 1D and depth-wise variations of the latter.
A high level overview of these combined methods is shown in Fig.~\ref{fig:highleveloverview}.
Although we choose the EEG epileptic seizure recognition dataset from University of California, Irvine (UCI)~\cite{andrzejak2001indications} for EEG classification, the implications of this study could be generalized in any kind of signal classification problem.
Here we also refer to CNN as a neural network consisting of alternating convolutional layers each one followed by a Rectified Linear Unit (ReLU) and a max pooling layer and a fully connected layer at the end while the term `layer' denotes the number of convolutional layers.

\section{DATA}
The UCI EEG epileptic seizure recognition dataset~\cite{andrzejak2001indications} consists of $500$ signals each one with $4097$ samples (23.5 seconds).
The dataset is annotated into five classes with $100$ signals for each class (in parenthesis the shortened label names used in Fig. \ref{fig:highleveloverview} and \ref{fig:signal2imageoutputs}):
\begin{enumerate}
	\item healthy patient while having his eyes open (Open),
	\item healthy patient while having his eyes closed (Closed),
	\item patient with tumor taken from healthy area (Healthy),
	\item patient with tumor taken from tumor area (Tumor),
	\item patient while having seizure activity (Epilepsy)
\end{enumerate}

For the purposes of this paper we use a variation of the database\footnote{\url{https://archive.ics.uci.edu/ml/datasets/Epileptic+Seizure+Recognition}} in which the EEG signals are split into segments with $178$ samples each, resulting in a balanced dataset that consists of $11500$ EEG signals.

\begin{figure}[!t]
	\centering
	\begin{tikzpicture}[]
		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{images/signal_epilepsy.png}};
		\node[align=left] at (-4.2, 0) {$x_i$};
		\draw[dashed,->] (-4, 0) -- (-3.8, 0);
		\node[draw, minimum height=2.55cm] at (-3.5, 0) {$m$};
		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{images/cnn_epilepsy.png}};
		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
		\node[draw, minimum height=2.55cm] at (0.1, 0) {$b_{d}$};
		\draw[dashed,->] (0.4, 0) -- (0.6, 0);
		\node[align=left] at (0.8, 0) {$\hat{y_i}$};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.67, 1.1) {\footnotesize Open 0.1\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.74, 0.55) {\footnotesize Closed 0.2\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.78, 0) {\footnotesize Healthy 0.9\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.8, -0.55) {\footnotesize Tumor 34.7\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.9, -1.1) {\footnotesize Epilepsy 64.1\%};
	\end{tikzpicture}
	\caption{High level overview of a feed-forward pass of the combined methods.
	$x_i$ is the input, $m$ is the Signal2Image module, $b_{d}$ is the 1D or 2D architecture `base model' for $d=1,2$ respectively and $\hat{y_i}$ is the predicted output.
	The names of the labels are depicted at the right along with the predictions for this example signal.
	The image between $m$ and $b_{d}$ depicts the output of the one layer CNN Signal2Image module, while the `signal as image' and spectrogram have intermediate images as those depicted at the second and third row of Fig.~\ref{fig:signal2imageoutputs}.
	Arrows denote the flow of the feed-forward pass.
	For the 1D architectures $m$ is omitted and no intermediate image is generated.}
	\label{fig:highleveloverview}
\end{figure}

\section{METHODS}
\subsection{Definitions}
We define the dataset $D=\{x_i, y_i\}_{i=1...N}$ where $x_i \in \mathbb{Z}^n$ and $y_i \in \{1, 2, 3, 4, 5\}$ denote the $i^{th}$ input signal with dimensionality $n=178$ and the $i^{th}$ label with five possible classes respectively.
$N=11500$ is the number of observations.

We also define the set of S2Is as $M$ and the member of this set as $m$ which include the following modules:
\begin{itemize}
	\item `signal as image' (non-trainable)
	\item spectrogram (non-trainable)
	\item one and two layers CNN (trainable)
\end{itemize}

We then define the set of `base models' as $B$ and the member of this set as $b_d$ where $d=[1,2]$ denotes the dimensionality of the convolutional, max pooling, batch normalization and adaptive average pooling layers.
$B$ includes the following $b_d$ along with their depth-wise variations and their equivalent 1D architectures for $d=1$ (for a complete list refer to first two rows of Table.~\ref{table:results}):
\begin{itemize}
	\item LeNet~\cite{lecun1998gradient}
	\item AlexNet~\cite{krizhevsky2012imagenet}
	\item VGGnet~\cite{simonyan2014very}
	\item ResNet~\cite{he2016deep}
	\item DenseNet~\cite{huang2017densely}
\end{itemize}

We finally define the combinations of $m$ and $b_d$ as the members $c$ of the set of combined models $C$.
Using the previous definitions, the aim of this paper is the evaluation of the set of models $C$, where $C$ is the combined set of $M$ and $B$ i.e. $C=M\times B$ w.r.t. time performance and class accuracy trained on $D$.

\subsection{Signal2Image Modules}
In this section we describe the internals of each S2I module.
For the `signal as image' module, we normalized the amplitude of $x_i$ to the range $[1, 178]$.
The results were inverted along the y-axis, rounded to the nearest integer and then they were used as the y-indices for the pixels with amplitude $255$ on a $178\times 178$ image initialized with zeros.

For the spectrogram module, which is used for visualizing the change of the frequency of a non-stationary signal over time~\cite{oppenheim1999discrete}, we used a Tukey window with a shape parameter of $0.25$, a segment length of $8$ samples, an overlap between segments of $4$ samples and a fast Fourier transform of $64$ samples to convert the $x_i$ into the time-frequency domain.
The resulted spectrogram, which represents the magnitude of the power spectral density ($V^2/Hz$) of $x_i$, was then upsampled to $178\times 178$ using bilinear pixel interpolation.

For the CNN modules with one and two layers, $x_i$ is converted to an image using learnable parameters instead of some static procedure.
The one layer module consists of one 1D convolutional layer (kernel sizes of $3$ with $8$ channels).
The two layer module consists of two 1D convolutional layers (kernel sizes of $3$ with $8$ and $16$ channels) with the first layer followed by a ReLU activation function and a 1D max pooling operation (kernel size of $2$).
The feature maps of the last convolutional layer for both modules are then concatenated along the y-axis and then resized to $178\times 178$ using bilinear interpolation.

We constrain the output for all $m$ to a $178\times 178$ image to enable visual comparison.
Three identical channels were also stacked for all $m$ outputs to satisfy the input size requirements for $b_d$.
Architectures of all $b_d$ remained the same, except for the number of the output nodes of the last linear layer which was set to five to correspond to the number of classes of $D$.
An example of the respective outputs of some of the $m$ (the one/two layers CNN produced similar visualizations) are depicted in the second, third and fourth row of Fig.~\ref{fig:signal2imageoutputs}.

\begin{figure*}[!t]
	\centering
	\rotatebox[origin=c]{90}{Original Signal}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{images/signal_eyes_open.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{images/signal_eyes_closed.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{images/signal_healthy_area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{images/signal_tumor_area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{images/signal_epilepsy.png}
	\end{subfigure}

	\rotatebox[origin=c]{90}{`Signal as Image'}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/signal_as_image_eyes_open.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/signal_as_image_eyes_closed.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/signal_as_image_healthy_area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/signal_as_image_tumor_area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/signal_as_image_epilepsy.png}
	\end{subfigure}

	\rotatebox[origin=c]{90}{Spectrogram}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/spectrogram_eyes_open.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/spectrogram_eyes_closed.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/spectrogram_healthy_area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/spectrogram_tumor_area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/spectrogram_epilepsy.png}
	\end{subfigure}

	\rotatebox[origin=c]{90}{\hspace{5mm} one layer CNN}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/cnn_eyes_open.png}
		\caption{Open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/cnn_eyes_closed.png}
		\caption{Closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/cnn_healthy_area.png}
		\caption{Healthy}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/cnn_tumor_area.png}
		\caption{Tumor}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{images/cnn_epilepsy.png}
		\caption{Epilepsy}
	\end{subfigure}
	\caption{Visualizations of the original signals and the outputs of the S2Is for each class.
	The x, y-axis of the first row are in \SI{}{\micro V} and time samples respectively.
	The x, y-axis of the rest of the subfigures denote spatial information, since we do not inform the `base model' the concept of time along the x-axis or the concept of frequency along the y-axis.
	Higher pixel intensity denotes higher amplitude.}
	\label{fig:signal2imageoutputs}
\end{figure*}

\subsection{Evaluation}
Convolutional layers of $m$ were initialized using Kaiming uniform~\cite{he2015delving}. Values are sampled from the uniform distribution $\mathcal{U}(-c, c)$, where $c$ is:
\begin{equation}
	c = \sqrt{\frac{6}{(1 + a^2) k}}
\end{equation}

\noindent
,$a$ in this study is set to zero and $k$ is the size of the input of the layer.
The linear layers of $m$ were initialized using $\mathcal{U}(-\frac{1}{\sqrt{k}},\frac{1}{\sqrt{k}})$.
The convolutional and linear layers of all $b_d$ were initialized according to their original implementation.

We used Adam~\cite{kingma2014adam} as the optimizer with learning rate $lr=0.001$, betas $b_1=0.9$, $b_2=0.999$, epsilon $\epsilon=10^{-8}$ without weight decay and cross entropy as the loss function.
Batch size was $20$ and no additional regularization was used besides the structural such as dropout layers that some of the `base models' (AlexNet, VGGnet and DenseNet) have.

Out of the 11500 signals we used $76\%$, $12\%$ and $12\%$ of the data ($8740,1380,1380$ signals) as training, validation and test data respectively.
No artifact handling or preprocessing was performed.
All networks were trained for $100$ epochs and model selection was performed using the best validation accuracy out of all the epochs.
We used PyTorch~\cite{paszke2017automatic} for implementing the neural network architectures and training/preprocessing was done using a NVIDIA Titan X Pascal GPU 12GB RAM and a 12 Core Intel i7-8700 CPU @ 3.20GHz on a Linux operating system.

\begin{table*}[!t]
	\caption{Test accuracies (\%) for combined models.
	The second row indicates the number of layers.
	Bold indicates the best accuracy for each base model.}
	\label{table:results}
	\begin{minipage}{\textwidth}
		\setlength\tabcolsep{1pt}
		\centering
		\input{results_table.tex}
	\end{minipage}
\end{table*}

\section{RESULTS}
As shown in Table.~\ref{table:results} the one layer CNN DenseNet201 achieved the best accuracy of $85.3\%$ with training time 70 seconds/epoch on average.
In overall the one layer CNN S2I achieved best accuracies for eleven out of fifteen `base models'.
The two layer CNN S2I achieved worse even compared with the 1D variants, indicating that increase of the S2I depth is not beneficial.
The `signal as image' and spectrogram S2Is performed much worse than 1D variants and the CNN S2Is.
The spectrogram S2I results are in contrary with the expectation that the interpretable time-frequency representation would help in finding good features for classification.
We hypothesize that the spectrogram S2I was hindered by its lack of non-trainable parameters.
Another outcome of these experiments is that increasing the depth of the base models did not increase the accuracy which is inline with previous results~\cite{schirrmeister2017deep}.

\section{CONCLUSIONS}
In this paper we have shown empirical evidence that 1D `base model' variations and trainable S2Is (especially the one layer CNN) perform better than non-trainable S2Is.
However more work needs to be done for full replacing non-trainable S2Is, not only from the scope of achieving higher accuracy results but also increasing the interpretability of the model.
Another point of reference is that the combined models were trained from scratch based on the hypothesis that pretrained low level features of the `base models' might not be suitable for spectrogram-like images such as those created by S2Is.
Future work could include testing this hypothesis by initializing a `base model' using transfer learning or other initialization methods.
Moreover, trainable S2Is and 1D `base model' variations could also be used for other physiological signals besides EEG such as Electrocardiography, Electromyography and Galvanic Skin Response.

\section*{ACKNOWLEDGMENT}
This work was supported by the European Union's Horizon 2020 research and innovation programme under Grant agreement 769574.
We gratefully acknowledge the support of NVIDIA with the donation of the Titan X Pascal GPU used for this research.

\bibliographystyle{IEEEtran}
\bibliography{ms}

\end{document}

### 2020-04-25 LeNet_2D.py

@@ -1,6 +1,6 @@
-import torch.nn as nn
 import torch.nn.functional as F
 
+from torch import nn
 
 class lenet_2D(nn.Module):
     def __init__(self):

### 2020-04-25 dataset.py

@@ -1,16 +1,19 @@
 import os
-import urllib
 import pandas as pd
 import torch
+import urllib
+
 from torch.utils.data.dataset import Dataset
 
 
 class UCI_epilepsy(Dataset):
-    def __init__(self, training_validation_test):
+    def __init__(self, training_validation_test, DEBUG):
         filename = "./data.csv"
         if not os.path.isfile(filename):
             urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
         dataset = pd.read_csv(filename)
+        if DEBUG:
+            dataset = dataset[:10]
         signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
         labels_all = dataset['y']
         last_training_index = int(signals_all.shape[0]*0.76)

### 2020-04-25 main.py

@@ -1,19 +1,22 @@
-#!/usr/bin/python
+#!/usr/bin/python3
 import collections
-import models_1D
+import numpy as np
 import os
-import pickle
-import signal2image_modules
+import pandas as pd
+import sys
 import time
 import torch
-import torch.nn as nn
 
+from torch import nn
 from torch.optim import Adam
 from torch.utils.data import DataLoader
 from torchvision import models
 
 from LeNet_2D import lenet_2D
 from dataset import UCI_epilepsy
+from models_1D import lenet, alexnet, vgg11, vgg13, vgg16, vgg19, resnet18, resnet34, resnet50, resnet101, resnet152, densenet121, densenet161, densenet169, densenet201
+from signal2image_modules import SignalAsImage, Spectrogram, CNN_one_layer, CNN_two_layers
+from utilities import save_signal, save_signal_as_image, save_spectrogram, save_cnn
 
 
 if __name__ == '__main__':
@@ -22,52 +25,60 @@ if __name__ == '__main__':
     if not os.path.exists('selected_models'):
         os.mkdir('selected_models')
     num_classes = 5
-    num_epochs = 100
     batch_size = 20
     signals_all_max = 2047
     signals_all_min = -1885
-    training_dataset = UCI_epilepsy('training')
-    validation_dataset = UCI_epilepsy('validation')
-    test_dataset = UCI_epilepsy('test')
+    if len(sys.argv) > 1:
+        DEBUG = True
+        num_epochs = 1
+        device = 'cpu'
+    else:
+        DEBUG = False
+        num_epochs = 100
+        device = 'cuda'
+    training_dataset = UCI_epilepsy('training', DEBUG)
+    validation_dataset = UCI_epilepsy('validation', DEBUG)
+    test_dataset = UCI_epilepsy('test', DEBUG)
     training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
     test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
     criterion = nn.CrossEntropyLoss()
     base_models_names = ['lenet', 'alexnet', 'vgg11', 'vgg13', 'vgg16', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201']
[…]

### 2020-04-25 read_results.py

@@ -1,15 +1,0 @@
-#!/usr/bin/python
-import pickle
-import numpy as np
-
-with open('results.pkl', 'rb') as f:
-    results_train_time_for_paper = np.zeros((75,))
-    results_test_accuracy_for_paper = np.zeros((75,))
-    results = pickle.load(f)
-    for index, model in enumerate(results):
-        results_train_time_for_paper[index] = np.around(results[model]['train_time']/100, 1)
-        results_test_accuracy_for_paper[index] = np.around(results[model]['test_accuracy'], 1)
-    results_train_time_for_paper = results_train_time_for_paper.reshape(5, 15)
-    results_test_accuracy_for_paper = results_test_accuracy_for_paper.reshape(5, 15)
-    print(" \\\\\n".join([" & ".join(map(str, line)) for line in results_train_time_for_paper]))
-    print(" \\\\\n".join([" & ".join(map(str, line)) for line in results_test_accuracy_for_paper]))

### 2020-04-25 signal2image_modules.py

@@ -1,7 +1,8 @@
 import torch
-import torch.nn as nn
 import torch.nn.functional as F
+
 from scipy.signal import spectrogram
+from torch import nn
 
 
 def replace_last_layer(base_model, combined_model_name, num_classes):
@@ -14,8 +15,9 @@ def replace_last_layer(base_model, combined_model_name, num_classes):
     return base_model
 
 class SignalAsImage(nn.Module):
-    def __init__(self, num_classes, base_model, combined_model_name, signals_all_max, signals_all_min):
+    def __init__(self, num_classes, base_model, combined_model_name, signals_all_max, signals_all_min, device):
         super(SignalAsImage, self).__init__()
+        self.device = device
         self.signals_all_max = signals_all_max
         self.signals_all_min = signals_all_min
         self.base_model = replace_last_layer(base_model, combined_model_name, num_classes)
@@ -24,7 +26,7 @@ class SignalAsImage(nn.Module):
         x = x - self.signals_all_min
         x = 178 * x / (self.signals_all_max - self.signals_all_min)
         x = x.floor().long()
-        out = torch.zeros(x.shape[0], 1, 178, 178).cuda()
+        out = torch.zeros(x.shape[0], 1, 178, 178, device=self.device)
         for index, _ in enumerate(x):
             out[index, 0, 177 - x[index, 0, :], range(178)] = 255
         out = torch.cat((out, out, out), 1)
@@ -33,12 +35,13 @@ class SignalAsImage(nn.Module):
 
 
 class Spectrogram(nn.Module):
-    def __init__(self, num_classes, base_model, combined_model_name):
+    def __init__(self, num_classes, base_model, combined_model_name, device):
         super(Spectrogram, self).__init__()
+        self.device = device
         self.base_model = replace_last_layer(base_model, combined_model_name, num_classes)
 
     def forward(self, x):
-        out = torch.zeros(x.shape[0], 1, 178, 178).cuda()
+        out = torch.zeros(x.shape[0], 1, 178, 178, device=self.device)
         for index, signal in enumerate(x):
             _, _, Sxx = spectrogram(signal.cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
             out[index, 0, :, :] = F.interpolate(torch.tensor(Sxx[0, :, :]).unsqueeze(0).unsqueeze(0), 178, mode='bilinear')

### 2020-04-25 utilities.py

@@ -1,0 +1,52 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import torch
+
+from PIL import Image
+from scipy.signal import spectrogram, resample
+
+
+def save_signal(signals_all, signal_index, label_name):
+    data = signals_all[signal_index].squeeze().cpu().detach().numpy()
+    plt.figure()
+    plt.plot(data, linewidth=4, color='k')
+    plt.axis('off')
+    plt.xlim([0, 177])
+    plt.ylim([-1000, 1000])
+    plt.savefig(f'./paper/images/signal_{label_name}.png', bbox_tight='tight')
+    plt.close()
+
+def save_signal_as_image(signals_all, signal_index, label_name):
+    signals_all_min = -1000
+    signals_all_max = 1000
+    x = signals_all[signal_index] - signals_all_min
+    x = 178 * x / (signals_all_max - signals_all_min)
+    x = x.squeeze(0).floor().long()
+    data = torch.zeros(178, 178)
+    for index in range(178):
+        data[177 - x[index], index] = 255
+    plt.figure()
+    plt.imsave(f'./paper/images/signal_as_image_{label_name}.png', data, cmap='gray')
+    plt.close()
+
+def save_spectrogram(signals_all, signal_index, label_name):
+    _, _, Sxx = spectrogram(signals_all[signal_index].cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
+    data = np.array(Image.fromarray(Sxx[0, :, :]).resize((178, 178), resample=1))
+    plt.figure()
+    plt.imsave(f'./paper/images/spectrogram_{label_name}.png', data, cmap='gray')
+    plt.close()
+
+def save_cnn(signals_all, signal_index, label_name):
+    model = torch.load('./selected_models/alexnet_cnn_one_layer.pt')
+    device = next(model.parameters()).device
+    signal = signals_all[signal_index].unsqueeze(0).to(device)
+    outputs= []
+    def hook(module, input, output):
+        outputs.append(output)
+    model.conv.register_forward_hook(hook)
+    model(signal)
+    data = outputs[0][0, 0].cpu().detach().numpy()
+    data = np.array(Image.fromarray(data).resize((178, 178), resample=1))
+    plt.figure()
+    plt.imsave(f'./paper/images/cnn_{label_name}.png', data, cmap='gray')
+    plt.close()

### 2020-04-25 visualize_paper.py

@@ -1,78 +1,0 @@
-#!/usr/bin/python
-import matplotlib.pyplot as plt
-import numpy as np
-import os
-import pandas as pd
-import torch
-
-from PIL import Image
-from scipy.signal import spectrogram, resample
-
-
-def save_signal(signal_index):
-    data = signals_all[signal_index].squeeze().squeeze().cpu().detach().numpy()
-    plt.figure()
-    plt.plot(data, linewidth=4, color='k')
-    plt.axis('off')
-    plt.xlim([0, 177])
-    plt.ylim([-1000, 1000])
-    plt.savefig('images/signal_{}.png'.format(labels_names[labels_all[signal_index]]), bbox_tight='tight')
-
-def save_signal_as_image(signal_index):
-    signals_all_min = -1000
-    signals_all_max = 1000
-    x = signals_all[signal_index] - signals_all_min
-    x = 178 * x / (signals_all_max - signals_all_min)
-    x = x.squeeze(0).floor().long()
-    data = torch.zeros(178, 178)
-    for index in range(178):
-        data[177 - x[index], index] = 255
-    plt.figure()
-    plt.imsave('images/signal_as_image_{}.png'.format(labels_names[labels_all[signal_index]]), data, cmap='gray')
-
-def save_spectrogram(signal_index):
-    _, _, Sxx = spectrogram(signals_all[signal_index].cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
-    data = np.array(Image.fromarray(Sxx[0, :, :]).resize((178, 178), resample=1))
-    plt.figure()
-    plt.imsave('images/spectrogram_{}.png'.format(labels_names[labels_all[signal_index]]), data, cmap='gray')
-
-def save_cnn(signal_index):
-    signal = signals_all[signal_index].unsqueeze_(0).cuda()
-    model = torch.load('selected_models/alexnet_cnn_one_layer.pt')
-    outputs= []
-    def hook(module, input, output):
-        outputs.append(output)
-    model.conv.register_forward_hook(hook)
-    _ = model(signal)
-    data = outputs[0][0, 0].cpu().detach().numpy()
-    data = np.array(Image.fromarray(data).resize((178, 178), resample=1))
-    plt.figure()
-    plt.imsave('images/cnn_{}.png'.format(labels_names[labels_all[signal_index]]), data, cmap='gray')
-
-def save_all(signal_index):
[…]

### 2020-04-27 dataset.py
simplify make procedure

@@ -7,13 +7,12 @@ from torch.utils.data.dataset import Dataset
 
 
 class UCI_epilepsy(Dataset):
-    def __init__(self, training_validation_test, DEBUG):
+    def __init__(self, training_validation_test, num_samples):
         filename = "./data.csv"
         if not os.path.isfile(filename):
             urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
         dataset = pd.read_csv(filename)
-        if DEBUG:
-            dataset = dataset[:10]
+        dataset = dataset[:num_samples]
         signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
         labels_all = dataset['y']
         last_training_index = int(signals_all.shape[0]*0.76)

### 2020-04-27 main.py

@@ -3,7 +3,7 @@ import collections
 import numpy as np
 import os
 import pandas as pd
-import sys
+import argparse
 import time
 import torch
 
@@ -22,23 +22,30 @@ from utilities import save_signal, save_signal_as_image, save_spectrogram, save_
 if __name__ == '__main__':
     torch.backends.cudnn.deterministic = True
     torch.manual_seed(0)
-    if not os.path.exists('selected_models'):
-        os.mkdir('selected_models')
+    path_models = './models'
+    if not os.path.exists(path_models):
+        os.mkdir(path_models)
     num_classes = 5
     batch_size = 20
     signals_all_max = 2047
     signals_all_min = -1885
-    if len(sys.argv) > 1:
-        DEBUG = True
-        num_epochs = 1
-        device = 'cpu'
-    else:
-        DEBUG = False
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--full', default=False, action='store_true')
+    parser.add_argument('--gpu', default=False, action='store_true')
+    args = parser.parse_args()
+    if args.full:
+        num_samples = 11500
         num_epochs = 100
+    else:
+        num_samples = 10
+        num_epochs = 1
+    if args.gpu:
         device = 'cuda'
-    training_dataset = UCI_epilepsy('training', DEBUG)
-    validation_dataset = UCI_epilepsy('validation', DEBUG)
-    test_dataset = UCI_epilepsy('test', DEBUG)
+    else:
+        device = 'cpu'
+    training_dataset = UCI_epilepsy('training', num_samples)
+    validation_dataset = UCI_epilepsy('validation', num_samples)
+    test_dataset = UCI_epilepsy('test', num_samples)
     training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
     test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
@@ -105,12 +112,12 @@ if __name__ == '__main__':
             results[combined_model_name]['validation_accuracy'].append(validation_accuracy)
             if validation_accuracy > best_validation_accuracy:
                 best_validation_accuracy = validation_accuracy
-                torch.save(model, f'selected_models/{combined_model_name}.pt')
+                torch.save(model, f'{path_models}/{combined_model_name}.pt')
                 print('saving as best model')
         train_time = time.time() - train_time
[…]

### 2020-04-27 utilities.py

@@ -36,8 +36,8 @@ def save_spectrogram(signals_all, signal_index, label_name):
     plt.imsave(f'./paper/images/spectrogram_{label_name}.png', data, cmap='gray')
     plt.close()
 
-def save_cnn(signals_all, signal_index, label_name):
-    model = torch.load('./selected_models/alexnet_cnn_one_layer.pt')
+def save_cnn(signals_all, signal_index, label_name, path_models):
+    model = torch.load(f'{path_models}/alexnet_cnn_one_layer.pt')
     device = next(model.parameters()).device
     signal = signals_all[signal_index].unsqueeze(0).to(device)
     outputs= []

### 2020-04-27 dataset.py
various fixes

@@ -7,8 +7,8 @@ from torch.utils.data.dataset import Dataset
 
 
 class UCI_epilepsy(Dataset):
-    def __init__(self, training_validation_test, num_samples):
-        filename = "./data.csv"
+    def __init__(self, training_validation_test, num_samples, path_tmp):
+        filename = f'{path_tmp}/data.csv'
         if not os.path.isfile(filename):
             urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
         dataset = pd.read_csv(filename)

### 2020-04-27 main.py

@@ -22,9 +22,15 @@ from utilities import save_signal, save_signal_as_image, save_spectrogram, save_
 if __name__ == '__main__':
     torch.backends.cudnn.deterministic = True
     torch.manual_seed(0)
-    path_models = './models'
+    path_tmp = './tmp'
+    if not os.path.exists(path_tmp):
+        os.mkdir(path_tmp)
+    path_models = f'{path_tmp}/models'
     if not os.path.exists(path_models):
         os.mkdir(path_models)
+    path_images = './paper/images'
+    if not os.path.exists(path_images):
+        os.mkdir(path_images)
     num_classes = 5
     batch_size = 20
     signals_all_max = 2047
@@ -43,9 +49,9 @@ if __name__ == '__main__':
         device = 'cuda'
     else:
         device = 'cpu'
-    training_dataset = UCI_epilepsy('training', num_samples)
-    validation_dataset = UCI_epilepsy('validation', num_samples)
-    test_dataset = UCI_epilepsy('test', num_samples)
+    training_dataset = UCI_epilepsy('training', num_samples, path_tmp)
+    validation_dataset = UCI_epilepsy('validation', num_samples, path_tmp)
+    test_dataset = UCI_epilepsy('test', num_samples, path_tmp)
     training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
     test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
@@ -147,9 +153,7 @@ if __name__ == '__main__':
     with open('paper/results_table.tex', 'w') as f:
         df.to_latex(buf=f, bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
-    if not os.path.exists('./paper/images'):
-        os.mkdir('./paper/images')
-    dataset = pd.read_csv('./data.csv')
+    dataset = pd.read_csv(f'{path_tmp}/data.csv')
     signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
     labels_all = dataset['y']
     signals_all = torch.tensor(signals_all.values, dtype=torch.float)

### 2020-04-28 main.py
fix Makefile

@@ -22,7 +22,7 @@ from utilities import save_signal, save_signal_as_image, save_spectrogram, save_
 if __name__ == '__main__':
     torch.backends.cudnn.deterministic = True
     torch.manual_seed(0)
-    path_tmp = './tmp'
+    path_tmp = 'tmp'
     if not os.path.exists(path_tmp):
         os.mkdir(path_tmp)
     path_models = f'{path_tmp}/models'
@@ -31,6 +31,9 @@ if __name__ == '__main__':
     path_images = './paper/images'
     if not os.path.exists(path_images):
         os.mkdir(path_images)
+    path_tables = './paper/tables'
+    if not os.path.exists(path_tables):
+        os.mkdir(path_tables)
     num_classes = 5
     batch_size = 20
     signals_all_max = 2047
@@ -150,7 +153,7 @@ if __name__ == '__main__':
     results_test_accuracy_for_paper = results_test_accuracy_for_paper.reshape(5, 15)
     df = pd.DataFrame(results_test_accuracy_for_paper, index=['1D', '2D, signal as image', '2D, spectrogram', '2D, one layer CNN', '2D, two layer CNN'])
     df.columns = base_models_names
-    with open('paper/results_table.tex', 'w') as f:
+    with open(f'{path_tables}/results.tex', 'w') as f:
         df.to_latex(buf=f, bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
     dataset = pd.read_csv(f'{path_tmp}/data.csv')

### 2020-06-04 ms.tex
simplify repo

--- 2020-04-25 paper/ms.tex
@@
 \IEEEoverridecommandlockouts
-\graphicspath{{./images/}}
+
+\pdfinfoomitdate=1
+\pdfsuppressptexinfo=-1
+\pdftrailerid{}
 
@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{images/signal_epilepsy.png}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{results/signal_epilepsy.png}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{images/cnn_epilepsy.png}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{results/cnn_epilepsy.png}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 		\centering
-		\includegraphics[scale=0.2]{images/signal_eyes_open.png}
+		\includegraphics[scale=0.2]{results/signal_eyes_open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{images/signal_eyes_closed.png}
+		\includegraphics[scale=0.2]{results/signal_eyes_closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{images/signal_healthy_area.png}
+		\includegraphics[scale=0.2]{results/signal_healthy_area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{images/signal_tumor_area.png}
+		\includegraphics[scale=0.2]{results/signal_tumor_area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{images/signal_epilepsy.png}
+		\includegraphics[scale=0.2]{results/signal_epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/signal_as_image_eyes_open.png}
+		\includegraphics[scale=0.5]{results/signal_as_image_eyes_open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/signal_as_image_eyes_closed.png}
+		\includegraphics[scale=0.5]{results/signal_as_image_eyes_closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/signal_as_image_healthy_area.png}
+		\includegraphics[scale=0.5]{results/signal_as_image_healthy_area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/signal_as_image_tumor_area.png}
+		\includegraphics[scale=0.5]{results/signal_as_image_tumor_area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/signal_as_image_epilepsy.png}
+		\includegraphics[scale=0.5]{results/signal_as_image_epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/spectrogram_eyes_open.png}
+		\includegraphics[scale=0.5]{results/spectrogram_eyes_open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/spectrogram_eyes_closed.png}
+		\includegraphics[scale=0.5]{results/spectrogram_eyes_closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/spectrogram_healthy_area.png}
+		\includegraphics[scale=0.5]{results/spectrogram_healthy_area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/spectrogram_tumor_area.png}
+		\includegraphics[scale=0.5]{results/spectrogram_tumor_area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/spectrogram_epilepsy.png}
+		\includegraphics[scale=0.5]{results/spectrogram_epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/cnn_eyes_open.png}
+		\includegraphics[scale=0.5]{results/cnn_eyes_open.png}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/cnn_eyes_closed.png}
+		\includegraphics[scale=0.5]{results/cnn_eyes_closed.png}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/cnn_healthy_area.png}
+		\includegraphics[scale=0.5]{results/cnn_healthy_area.png}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/cnn_tumor_area.png}
+		\includegraphics[scale=0.5]{results/cnn_tumor_area.png}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{images/cnn_epilepsy.png}
+		\includegraphics[scale=0.5]{results/cnn_epilepsy.png}
 		\caption{Epilepsy}
@@
 	\begin{minipage}{\textwidth}
-		\setlength\tabcolsep{1pt}
+		\setlength\tabcolsep{0.6pt}
 		\centering
-		\input{results_table.tex}
+		\input{results/results.tex}
 	\end{minipage}

### 2020-06-04 main.py

@@ -28,12 +28,9 @@ if __name__ == '__main__':
     path_models = f'{path_tmp}/models'
     if not os.path.exists(path_models):
         os.mkdir(path_models)
-    path_images = './paper/images'
-    if not os.path.exists(path_images):
-        os.mkdir(path_images)
-    path_tables = './paper/tables'
-    if not os.path.exists(path_tables):
-        os.mkdir(path_tables)
+    path_results = 'results'
+    if not os.path.exists(path_results):
+        os.mkdir(path_results)
     num_classes = 5
     batch_size = 20
     signals_all_max = 2047
@@ -153,7 +150,7 @@ if __name__ == '__main__':
     results_test_accuracy_for_paper = results_test_accuracy_for_paper.reshape(5, 15)
     df = pd.DataFrame(results_test_accuracy_for_paper, index=['1D', '2D, signal as image', '2D, spectrogram', '2D, one layer CNN', '2D, two layer CNN'])
     df.columns = base_models_names
-    with open(f'{path_tables}/results.tex', 'w') as f:
+    with open(f'{path_results}/results.tex', 'w') as f:
         df.to_latex(buf=f, bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
     dataset = pd.read_csv(f'{path_tmp}/data.csv')
@@ -164,7 +161,7 @@ if __name__ == '__main__':
     labels_names = ['eyes_open', 'eyes_closed', 'healthy_area', 'tumor_area', 'epilepsy']
     for index, label_name in enumerate(labels_names):
         signal_index = (labels_all == index).nonzero()[-1]
-        save_signal(signals_all, signal_index, label_name)
-        save_signal_as_image(signals_all, signal_index, label_name)
-        save_spectrogram(signals_all, signal_index, label_name)
-        save_cnn(signals_all, signal_index, label_name, path_models)
+        save_signal(signals_all, signal_index, label_name, path_results)
+        save_signal_as_image(signals_all, signal_index, label_name, path_results)
+        save_spectrogram(signals_all, signal_index, label_name, path_results)
+        save_cnn(signals_all, signal_index, label_name, path_models, path_results)

### 2020-06-04 utilities.py

@@ -6,17 +6,17 @@ from PIL import Image
 from scipy.signal import spectrogram, resample
 
 
-def save_signal(signals_all, signal_index, label_name):
+def save_signal(signals_all, signal_index, label_name, path_results):
     data = signals_all[signal_index].squeeze().cpu().detach().numpy()
     plt.figure()
     plt.plot(data, linewidth=4, color='k')
     plt.axis('off')
     plt.xlim([0, 177])
     plt.ylim([-1000, 1000])
-    plt.savefig(f'./paper/images/signal_{label_name}.png', bbox_tight='tight')
+    plt.savefig(f'{path_results}/signal_{label_name}.png', bbox_tight='tight')
     plt.close()
 
-def save_signal_as_image(signals_all, signal_index, label_name):
+def save_signal_as_image(signals_all, signal_index, label_name, path_results):
     signals_all_min = -1000
     signals_all_max = 1000
     x = signals_all[signal_index] - signals_all_min
@@ -26,17 +26,17 @@ def save_signal_as_image(signals_all, signal_index, label_name):
     for index in range(178):
         data[177 - x[index], index] = 255
     plt.figure()
-    plt.imsave(f'./paper/images/signal_as_image_{label_name}.png', data, cmap='gray')
+    plt.imsave(f'{path_results}/signal_as_image_{label_name}.png', data, cmap='gray')
     plt.close()
 
-def save_spectrogram(signals_all, signal_index, label_name):
+def save_spectrogram(signals_all, signal_index, label_name, path_results):
     _, _, Sxx = spectrogram(signals_all[signal_index].cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
     data = np.array(Image.fromarray(Sxx[0, :, :]).resize((178, 178), resample=1))
     plt.figure()
-    plt.imsave(f'./paper/images/spectrogram_{label_name}.png', data, cmap='gray')
+    plt.imsave(f'{path_results}/spectrogram_{label_name}.png', data, cmap='gray')
     plt.close()
 
-def save_cnn(signals_all, signal_index, label_name, path_models):
+def save_cnn(signals_all, signal_index, label_name, path_models, path_results):
     model = torch.load(f'{path_models}/alexnet_cnn_one_layer.pt')
     device = next(model.parameters()).device
     signal = signals_all[signal_index].unsqueeze(0).to(device)
[…]

### 2020-06-05 main.py
saved models belong to the results folder

@@ -25,9 +25,6 @@ if __name__ == '__main__':
     path_tmp = 'tmp'
     if not os.path.exists(path_tmp):
         os.mkdir(path_tmp)
-    path_models = f'{path_tmp}/models'
-    if not os.path.exists(path_models):
-        os.mkdir(path_models)
     path_results = 'results'
     if not os.path.exists(path_results):
         os.mkdir(path_results)
@@ -118,12 +115,12 @@ if __name__ == '__main__':
             results[combined_model_name]['validation_accuracy'].append(validation_accuracy)
             if validation_accuracy > best_validation_accuracy:
                 best_validation_accuracy = validation_accuracy
-                torch.save(model, f'{path_models}/{combined_model_name}.pt')
+                torch.save(model, f'{path_results}/{combined_model_name}.pt')
                 print('saving as best model')
         train_time = time.time() - train_time
         results[combined_model_name]['train_time'] = train_time
     for combined_model_name in combined_models_names:
-        model = torch.load(f'{path_models}/{combined_model_name}.pt')
+        model = torch.load(f'{path_results}/{combined_model_name}.pt')
         model.eval()
         test_loss_sum = 0
         corrects = 0
@@ -164,4 +161,4 @@ if __name__ == '__main__':
         save_signal(signals_all, signal_index, label_name, path_results)
         save_signal_as_image(signals_all, signal_index, label_name, path_results)
         save_spectrogram(signals_all, signal_index, label_name, path_results)
-        save_cnn(signals_all, signal_index, label_name, path_models, path_results)
+        save_cnn(signals_all, signal_index, label_name, path_results)

### 2020-06-05 utilities.py

@@ -36,8 +36,8 @@ def save_spectrogram(signals_all, signal_index, label_name, path_results):
     plt.imsave(f'{path_results}/spectrogram_{label_name}.png', data, cmap='gray')
     plt.close()
 
-def save_cnn(signals_all, signal_index, label_name, path_models, path_results):
-    model = torch.load(f'{path_models}/alexnet_cnn_one_layer.pt')
+def save_cnn(signals_all, signal_index, label_name, path_results):
+    model = torch.load(f'{path_results}/alexnet_cnn_one_layer.pt')
     device = next(model.parameters()).device
     signal = signals_all[signal_index].unsqueeze(0).to(device)
     outputs= []

### 2020-06-05 dataset.py
rename path_tmp to path_cache

@@ -7,8 +7,8 @@ from torch.utils.data import Dataset
 
 
 class UCI_epilepsy(Dataset):
-    def __init__(self, training_validation_test, num_samples, path_tmp):
-        filename = f'{path_tmp}/data.csv'
+    def __init__(self, training_validation_test, num_samples, path_cache):
+        filename = f'{path_cache}/data.csv'
         if not os.path.isfile(filename):
             urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
         dataset = pd.read_csv(filename)

### 2020-06-05 main.py

@@ -22,9 +22,9 @@ from utilities import save_signal, save_signal_as_image, save_spectrogram, save_
 if __name__ == '__main__':
     torch.backends.cudnn.deterministic = True
     torch.manual_seed(0)
-    path_tmp = 'tmp'
-    if not os.path.exists(path_tmp):
-        os.mkdir(path_tmp)
+    path_cache = 'cache'
+    if not os.path.exists(path_cache):
+        os.mkdir(path_cache)
     path_results = 'results'
     if not os.path.exists(path_results):
         os.mkdir(path_results)
@@ -46,9 +46,9 @@ if __name__ == '__main__':
         device = 'cuda'
     else:
         device = 'cpu'
-    training_dataset = UCI_epilepsy('training', num_samples, path_tmp)
-    validation_dataset = UCI_epilepsy('validation', num_samples, path_tmp)
-    test_dataset = UCI_epilepsy('test', num_samples, path_tmp)
+    training_dataset = UCI_epilepsy('training', num_samples, path_cache)
+    validation_dataset = UCI_epilepsy('validation', num_samples, path_cache)
+    test_dataset = UCI_epilepsy('test', num_samples, path_cache)
     training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
     test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
@@ -150,7 +150,7 @@ if __name__ == '__main__':
     with open(f'{path_results}/results.tex', 'w') as f:
         df.to_latex(buf=f, bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
-    dataset = pd.read_csv(f'{path_tmp}/data.csv')
+    dataset = pd.read_csv(f'{path_cache}/data.csv')
     signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
     labels_all = dataset['y']
     signals_all = torch.tensor(signals_all.values, dtype=torch.float)

### 2020-06-30 ms.tex
change filename convention to hyphen

@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{results/signal_epilepsy.png}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{results/signal-epilepsy}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{results/cnn_epilepsy.png}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{results/cnn-epilepsy}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal_eyes_open.png}
+		\includegraphics[scale=0.2]{results/signal-eyes-open}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal_eyes_closed.png}
+		\includegraphics[scale=0.2]{results/signal-eyes-closed}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal_healthy_area.png}
+		\includegraphics[scale=0.2]{results/signal-healthy-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal_tumor_area.png}
+		\includegraphics[scale=0.2]{results/signal-tumor-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal_epilepsy.png}
+		\includegraphics[scale=0.2]{results/signal-epilepsy}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal_as_image_eyes_open.png}
+		\includegraphics[scale=0.5]{results/signal-as-image-eyes-open}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal_as_image_eyes_closed.png}
+		\includegraphics[scale=0.5]{results/signal-as-image-eyes-closed}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal_as_image_healthy_area.png}
+		\includegraphics[scale=0.5]{results/signal-as-image-healthy-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal_as_image_tumor_area.png}
+		\includegraphics[scale=0.5]{results/signal-as-image-tumor-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal_as_image_epilepsy.png}
+		\includegraphics[scale=0.5]{results/signal-as-image-epilepsy}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram_eyes_open.png}
+		\includegraphics[scale=0.5]{results/spectrogram-eyes-open}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram_eyes_closed.png}
+		\includegraphics[scale=0.5]{results/spectrogram-eyes-closed}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram_healthy_area.png}
+		\includegraphics[scale=0.5]{results/spectrogram-healthy-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram_tumor_area.png}
+		\includegraphics[scale=0.5]{results/spectrogram-tumor-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram_epilepsy.png}
+		\includegraphics[scale=0.5]{results/spectrogram-epilepsy}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn_eyes_open.png}
+		\includegraphics[scale=0.5]{results/cnn-eyes-open}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn_eyes_closed.png}
+		\includegraphics[scale=0.5]{results/cnn-eyes-closed}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn_healthy_area.png}
+		\includegraphics[scale=0.5]{results/cnn-healthy-area}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn_tumor_area.png}
+		\includegraphics[scale=0.5]{results/cnn-tumor-area}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn_epilepsy.png}
+		\includegraphics[scale=0.5]{results/cnn-epilepsy}
 		\caption{Epilepsy}

### 2020-06-30 main.py

@@ -54,11 +54,11 @@ if __name__ == '__main__':
     base_models_names = ['lenet', 'alexnet', 'vgg11', 'vgg13', 'vgg16', 'vgg19', 'resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152', 'densenet121', 'densenet161', 'densenet169', 'densenet201']
     base_models_1D = [lenet, alexnet, vgg11, vgg13, vgg16, vgg19, resnet18, resnet34, resnet50, resnet101, resnet152, densenet121, densenet161, densenet169, densenet201]
     base_models_2D = [lenet_2D, models.alexnet, models.vgg11, models.vgg13, models.vgg16, models.vgg19, models.resnet18, models.resnet34, models.resnet50, models.resnet101, models.resnet152, models.densenet121, models.densenet161, models.densenet169, models.densenet201]
-    base_models_1D_names = [f'{model_name}_1D' for model_name in base_models_names]
-    combined_models_signal_as_image_names = [f'{model_name}_signal_as_image' for model_name in base_models_names]
-    combined_models_spectrogram_names = [f'{model_name}_spectrogram' for model_name in base_models_names]
-    combined_models_cnn_one_layer_names = [f'{model_name}_cnn_one_layer' for model_name in base_models_names]
-    combined_models_cnn_two_layers_names = [f'{model_name}_cnn_two_layers' for model_name in base_models_names]
+    base_models_1D_names = [f'{model_name}-1D' for model_name in base_models_names]
+    combined_models_signal_as_image_names = [f'{model_name}-signal-as-image' for model_name in base_models_names]
+    combined_models_spectrogram_names = [f'{model_name}-spectrogram' for model_name in base_models_names]
+    combined_models_cnn_one_layer_names = [f'{model_name}-cnn-one-layer' for model_name in base_models_names]
+    combined_models_cnn_two_layers_names = [f'{model_name}-cnn-two-layers' for model_name in base_models_names]
     base_models = base_models_1D + base_models_2D + base_models_2D + base_models_2D + base_models_2D
     combined_models_names = base_models_1D_names + combined_models_signal_as_image_names + combined_models_spectrogram_names + combined_models_cnn_one_layer_names + combined_models_cnn_two_layers_names
     results = collections.defaultdict(dict)
@@ -67,15 +67,15 @@ if __name__ == '__main__':
         results[combined_model_name]['validation_loss'] = []
         results[combined_model_name]['validation_accuracy'] = []
[…]

### 2020-06-30 utilities.py

@@ -13,7 +13,7 @@ def save_signal(signals_all, signal_index, label_name, path_results):
     plt.axis('off')
     plt.xlim([0, 177])
     plt.ylim([-1000, 1000])
-    plt.savefig(f'{path_results}/signal_{label_name}.png', bbox_tight='tight')
+    plt.savefig(f'{path_results}/signal-{label_name}.png', bbox_tight='tight')
     plt.close()
 
 def save_signal_as_image(signals_all, signal_index, label_name, path_results):
@@ -26,18 +26,18 @@ def save_signal_as_image(signals_all, signal_index, label_name, path_results):
     for index in range(178):
         data[177 - x[index], index] = 255
     plt.figure()
-    plt.imsave(f'{path_results}/signal_as_image_{label_name}.png', data, cmap='gray')
+    plt.imsave(f'{path_results}/signal-as-image-{label_name}.png', data, cmap='gray')
     plt.close()
 
 def save_spectrogram(signals_all, signal_index, label_name, path_results):
     _, _, Sxx = spectrogram(signals_all[signal_index].cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
     data = np.array(Image.fromarray(Sxx[0, :, :]).resize((178, 178), resample=1))
     plt.figure()
-    plt.imsave(f'{path_results}/spectrogram_{label_name}.png', data, cmap='gray')
+    plt.imsave(f'{path_results}/spectrogram-{label_name}.png', data, cmap='gray')
     plt.close()
 
 def save_cnn(signals_all, signal_index, label_name, path_results):
-    model = torch.load(f'{path_results}/alexnet_cnn_one_layer.pt')
+    model = torch.load(f'{path_results}/alexnet-cnn-one-layer.pt')
     device = next(model.parameters()).device
     signal = signals_all[signal_index].unsqueeze(0).to(device)
     outputs= []
@@ -48,5 +48,5 @@ def save_cnn(signals_all, signal_index, label_name, path_results):
     data = outputs[0][0, 0].cpu().detach().numpy()
     data = np.array(Image.fromarray(data).resize((178, 178), resample=1))
     plt.figure()
-    plt.imsave(f'{path_results}/cnn_{label_name}.png', data, cmap='gray')
+    plt.imsave(f'{path_results}/cnn-{label_name}.png', data, cmap='gray')
     plt.close()

### 2020-11-11 LeNet_2D.py
init

@@ -1,0 +1,23 @@
+import torch.nn.functional as F
+
+from torch import nn
+
+class lenet_2D(nn.Module):
+    def __init__(self):
+        super(lenet_2D, self).__init__()
+        self.conv1 = nn.Conv2d(3, 3, 5)
+        self.conv2 = nn.Conv2d(3, 16, 5)
+        self.fc1 = nn.Linear(41 * 41 * 16, 120)
+        self.fc2 = nn.Linear(120, 84)
+        self.fc3 = nn.Linear(84, 5)
+
+    def forward(self, x):
+        out = F.relu(self.conv1(x))
+        out = F.max_pool2d(out, 2)
+        out = F.relu(self.conv2(out))
+        out = F.max_pool2d(out, 2)
+        out = out.view(out.size(0), -1)
+        out = F.relu(self.fc1(out))
+        out = F.relu(self.fc2(out))
+        out = self.fc3(out)
+        return out

### 2020-11-11 dataset.py

@@ -1,0 +1,35 @@
+import os
+import pandas as pd
+import torch
+import urllib
+
+from torch.utils.data import Dataset
+
+
+class UCI_epilepsy(Dataset):
+    def __init__(self, training_validation_test, num_samples, cache_dir):
+        filename = f'{cache_dir}/data.csv'
+        if not os.path.isfile(filename):
+            urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
+        dataset = pd.read_csv(filename)
+        dataset = dataset[:num_samples]
+        signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
+        labels_all = dataset['y']
+        last_training_index = int(signals_all.shape[0]*0.76)
+        last_validation_index = int(signals_all.shape[0]*0.88)
+        if training_validation_test == 'training':
+            self.data = torch.tensor(signals_all.values[:last_training_index, :], dtype=torch.float)
+            self.labels = torch.tensor(labels_all[:last_training_index].values) - 1
+        elif training_validation_test == 'validation':
+            self.data = torch.tensor(signals_all.values[last_training_index:last_validation_index, :], dtype=torch.float)
+            self.labels = torch.tensor(labels_all[last_training_index:last_validation_index].values) - 1
+        elif training_validation_test == 'test':
+            self.data = torch.tensor(signals_all.values[last_validation_index:, :], dtype=torch.float)
+            self.labels = torch.tensor(labels_all[last_validation_index:].values) - 1
+        self.data.unsqueeze_(1)
+
+    def __getitem__(self, index):
+        return (self.data[index], self.labels[index])
+
+    def __len__(self):
+        return self.labels.shape[0]

### 2020-11-11 main.py

@@ -1,0 +1,159 @@
+import argparse
+import collections
+import numpy as np
+import os
+import pandas as pd
+import torch
+
+from torch import nn
+from torch.optim import Adam
+from torch.utils.data import DataLoader
+from torchvision import models
+
+from LeNet_2D import lenet_2D
+from dataset import UCI_epilepsy
+from models_1D import lenet, alexnet, vgg11, vgg13, vgg16, vgg19, resnet18, resnet34, resnet50, resnet101, resnet152, densenet121, densenet161, densenet169, densenet201
+from signal2image_modules import SignalAsImage, Spectrogram, CNN_one_layer, CNN_two_layers
+from utilities import save_signal, save_signal_as_image, save_spectrogram, save_cnn
+
+
+if __name__ == '__main__':
+    # DO NOT EDIT BLOCK
+    np.random.seed(0)
+    torch.backends.cudnn.benchmark = False
+    torch.backends.cudnn.deterministic = True
+    torch.manual_seed(0)
+
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--full', default=False, action='store_true')
+    args = parser.parse_args()
+
+    cache_dir = 'cache'
+    results_dir = 'results'
+    # END OF DO NOT EDIT BLOCK
+
+    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+    if args.full:
+        num_samples = 11500
+        num_epochs = 100
+    else:
+        num_samples = 10
+        num_epochs = 1
+    num_classes = 5
+    batch_size = 20
+    signals_all_max = 2047
+    signals_all_min = -1885
+    training_dataset = UCI_epilepsy('training', num_samples, cache_dir)
+    validation_dataset = UCI_epilepsy('validation', num_samples, cache_dir)
+    test_dataset = UCI_epilepsy('test', num_samples, cache_dir)
+    training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
+    validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
+    test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
+    criterion = nn.CrossEntropyLoss()
[…]

### 2020-11-11 signal2image_modules.py

@@ -1,0 +1,83 @@
+import torch
+import torch.nn.functional as F
+
+from scipy.signal import spectrogram
+from torch import nn
+
+
+def replace_last_layer(base_model, combined_model_name, num_classes):
+    if combined_model_name.startswith(('alexnet', 'vgg11', 'vgg13', 'vgg16', 'vgg19')):
+        base_model.classifier[-1] = nn.Linear(base_model.classifier[-1].in_features, num_classes)
+    elif combined_model_name.startswith(('resnet18', 'resnet34', 'resnet50', 'resnet101', 'resnet152')):
+        base_model.fc = nn.Linear(base_model.fc.in_features, num_classes)
+    elif combined_model_name.startswith(('densenet121', 'densenet161', 'densenet169', 'densenet201')):
+        base_model.classifier = nn.Linear(base_model.classifier.in_features, num_classes)
+    return base_model
+
+class SignalAsImage(nn.Module):
+    def __init__(self, num_classes, base_model, combined_model_name, signals_all_max, signals_all_min, device):
+        super(SignalAsImage, self).__init__()
+        self.device = device
+        self.signals_all_max = signals_all_max
+        self.signals_all_min = signals_all_min
+        self.base_model = replace_last_layer(base_model, combined_model_name, num_classes)
+
+    def forward(self, x):
+        x = x - self.signals_all_min
+        x = 178 * x / (self.signals_all_max - self.signals_all_min)
+        x = x.floor().long()
+        out = torch.zeros(x.shape[0], 1, 178, 178, device=self.device)
+        for index, _ in enumerate(x):
+            out[index, 0, 177 - x[index, 0, :], range(178)] = 255
+        out = torch.cat((out, out, out), 1)
+        out = self.base_model(out)
+        return out
+
+
+class Spectrogram(nn.Module):
+    def __init__(self, num_classes, base_model, combined_model_name, device):
+        super(Spectrogram, self).__init__()
+        self.device = device
+        self.base_model = replace_last_layer(base_model, combined_model_name, num_classes)
+
+    def forward(self, x):
+        out = torch.zeros(x.shape[0], 1, 178, 178, device=self.device)
+        for index, signal in enumerate(x):
+            _, _, Sxx = spectrogram(signal.cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
[…]

### 2020-11-11 utilities.py

@@ -1,0 +1,52 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import torch
+
+from PIL import Image
+from scipy.signal import spectrogram, resample
+
+
+def save_signal(signals_all, signal_index, label_name, results_dir):
+    data = signals_all[signal_index].squeeze().cpu().detach().numpy()
+    plt.figure()
+    plt.plot(data, linewidth=4, color='k')
+    plt.axis('off')
+    plt.xlim([0, 177])
+    plt.ylim([-1000, 1000])
+    plt.savefig(f'{results_dir}/signal-{label_name}.png')
+    plt.close()
+
+def save_signal_as_image(signals_all, signal_index, label_name, results_dir):
+    signals_all_min = -1000
+    signals_all_max = 1000
+    x = signals_all[signal_index] - signals_all_min
+    x = 178 * x / (signals_all_max - signals_all_min)
+    x = x.squeeze(0).floor().long()
+    data = torch.zeros(178, 178)
+    for index in range(178):
+        data[177 - x[index], index] = 255
+    plt.figure()
+    plt.imsave(f'{results_dir}/signal-as-image-{label_name}.png', data, cmap='gray')
+    plt.close()
+
+def save_spectrogram(signals_all, signal_index, label_name, results_dir):
+    _, _, Sxx = spectrogram(signals_all[signal_index].cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
+    data = np.array(Image.fromarray(Sxx[0, :, :]).resize((178, 178), resample=1))
+    plt.figure()
+    plt.imsave(f'{results_dir}/spectrogram-{label_name}.png', data, cmap='gray')
+    plt.close()
+
+def save_cnn(signals_all, signal_index, label_name, results_dir):
+    model = torch.load(f'{results_dir}/alexnet-cnn-one-layer.pt')
+    device = next(model.parameters()).device
+    signal = signals_all[signal_index].unsqueeze(0).to(device)
+    outputs= []
+    def hook(module, input, output):
+        outputs.append(output)
+    model.conv.register_forward_hook(hook)
+    model(signal)
+    data = outputs[0][0, 0].cpu().detach().numpy()
+    data = np.array(Image.fromarray(data).resize((178, 178), resample=1))
+    plt.figure()
+    plt.imsave(f'{results_dir}/cnn-{label_name}.png', data, cmap='gray')
+    plt.close()

### 2020-11-14 main.py
move variables in Makefile

@@ -25,11 +25,10 @@ if __name__ == '__main__':
     torch.manual_seed(0)
 
     parser = argparse.ArgumentParser()
+    parser.add_argument('cache_dir')
+    parser.add_argument('results_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
-
-    cache_dir = 'cache'
-    results_dir = 'results'
     # END OF DO NOT EDIT BLOCK
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
@@ -43,9 +42,9 @@ if __name__ == '__main__':
     batch_size = 20
     signals_all_max = 2047
     signals_all_min = -1885
-    training_dataset = UCI_epilepsy('training', num_samples, cache_dir)
-    validation_dataset = UCI_epilepsy('validation', num_samples, cache_dir)
-    test_dataset = UCI_epilepsy('test', num_samples, cache_dir)
+    training_dataset = UCI_epilepsy('training', num_samples, args.cache_dir)
+    validation_dataset = UCI_epilepsy('validation', num_samples, args.cache_dir)
+    test_dataset = UCI_epilepsy('test', num_samples, args.cache_dir)
     training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
     test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
@@ -111,9 +110,9 @@ if __name__ == '__main__':
             results[combined_model_name]['validation_accuracy'].append(validation_accuracy)
             if validation_accuracy > best_validation_accuracy:
                 best_validation_accuracy = validation_accuracy
-                torch.save(model, f'{results_dir}/{combined_model_name}.pt')
+                torch.save(model, f'{args.results_dir}/{combined_model_name}.pt')
                 print('saving as best model')
-        model = torch.load(f'{results_dir}/{combined_model_name}.pt')
+        model = torch.load(f'{args.results_dir}/{combined_model_name}.pt')
         model.eval()
         test_loss_sum = 0
         corrects = 0
@@ -134,7 +133,7 @@ if __name__ == '__main__':
         results[combined_model_name]['test_accuracy'] = test_accuracy
[…]

### 2020-11-29 main.py
simplify Makefile

@@ -20,8 +20,8 @@ from utilities import save_signal, save_signal_as_image, save_spectrogram, save_
 if __name__ == '__main__':
     # DO NOT EDIT BLOCK - Required by the Makefile
     parser = argparse.ArgumentParser()
-    parser.add_argument('cache_dir')
     parser.add_argument('results_dir')
+    parser.add_argument('tmp_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
     # END OF DO NOT EDIT BLOCK
@@ -43,9 +43,9 @@ if __name__ == '__main__':
     batch_size = 20
     signals_all_max = 2047
     signals_all_min = -1885
-    training_dataset = UCI_epilepsy('training', num_samples, args.cache_dir)
-    validation_dataset = UCI_epilepsy('validation', num_samples, args.cache_dir)
-    test_dataset = UCI_epilepsy('test', num_samples, args.cache_dir)
+    training_dataset = UCI_epilepsy('training', num_samples, args.tmp_dir)
+    validation_dataset = UCI_epilepsy('validation', num_samples, args.tmp_dir)
+    test_dataset = UCI_epilepsy('test', num_samples, args.tmp_dir)
     training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
     test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
@@ -145,7 +145,7 @@ if __name__ == '__main__':
     with open(f'{args.results_dir}/results.tex', 'w') as f:
         df.to_latex(buf=f, bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
-    dataset = pd.read_csv(f'{args.cache_dir}/data.csv')
+    dataset = pd.read_csv(f'{args.tmp_dir}/data.csv')
     signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
     labels_all = dataset['y']
     signals_all = torch.tensor(signals_all.values, dtype=torch.float)

### 2020-11-29 dataset.py
fix dirs in Makefile

@@ -7,8 +7,8 @@ from torch.utils.data import Dataset
 
 
 class UCI_epilepsy(Dataset):
-    def __init__(self, training_validation_test, num_samples, cache_dir):
-        filename = f'{cache_dir}/data.csv'
+    def __init__(self, training_validation_test, num_samples, tmp_dir):
+        filename = f'{tmp_dir}/data.csv'
         if not os.path.isfile(filename):
             urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
         dataset = pd.read_csv(filename)

### 2020-11-29 main.py

@@ -111,9 +111,9 @@ if __name__ == '__main__':
             results[combined_model_name]['validation_accuracy'].append(validation_accuracy)
             if validation_accuracy > best_validation_accuracy:
                 best_validation_accuracy = validation_accuracy
-                torch.save(model, f'{args.results_dir}/{combined_model_name}.pt')
+                torch.save(model, f'{args.tmp_dir}/{combined_model_name}.pt')
                 print('saving as best model')
-        model = torch.load(f'{args.results_dir}/{combined_model_name}.pt')
+        model = torch.load(f'{args.tmp_dir}/{combined_model_name}.pt')
         model.eval()
         test_loss_sum = 0
         corrects = 0
@@ -134,7 +134,7 @@ if __name__ == '__main__':
         results[combined_model_name]['test_accuracy'] = test_accuracy
         print(f'Model: {combined_model_name}, Epoch: {epoch}, Loss: {test_loss:.3f}, Accuracy: {test_accuracy:.2f}%')
         if combined_model_name != 'alexnet-cnn-one-layer':
-            os.remove(f'{args.results_dir}/{combined_model_name}.pt')
+            os.remove(f'{args.tmp_dir}/{combined_model_name}.pt')
 
     results_test_accuracy_for_paper = np.zeros((75,))
     for index, model in enumerate(results):
@@ -142,8 +142,7 @@ if __name__ == '__main__':
     results_test_accuracy_for_paper = results_test_accuracy_for_paper.reshape(5, 15)
     df = pd.DataFrame(results_test_accuracy_for_paper, index=['1D', '2D, signal as image', '2D, spectrogram', '2D, one layer CNN', '2D, two layer CNN'])
     df.columns = base_models_names
-    with open(f'{args.results_dir}/results.tex', 'w') as f:
-        df.to_latex(buf=f, bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
+    df.to_latex(f'{args.results_dir}/results.tex', bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
     dataset = pd.read_csv(f'{args.tmp_dir}/data.csv')
     signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
@@ -156,4 +155,4 @@ if __name__ == '__main__':
         save_signal(signals_all, signal_index, label_name, args.results_dir)
         save_signal_as_image(signals_all, signal_index, label_name, args.results_dir)
[…]

### 2020-11-29 utilities.py

@@ -36,8 +36,8 @@ def save_spectrogram(signals_all, signal_index, label_name, results_dir):
     plt.imsave(f'{results_dir}/spectrogram-{label_name}.png', data, cmap='gray')
     plt.close()
 
-def save_cnn(signals_all, signal_index, label_name, results_dir):
-    model = torch.load(f'{results_dir}/alexnet-cnn-one-layer.pt')
+def save_cnn(signals_all, signal_index, label_name, results_dir, tmp_dir):
+    model = torch.load(f'{tmp_dir}/alexnet-cnn-one-layer.pt')
     device = next(model.parameters()).device
     signal = signals_all[signal_index].unsqueeze(0).to(device)
     outputs= []

### 2020-11-30 ms.tex
init
fix README.md
simplify Makefile

@@
 \IEEEoverridecommandlockouts
-
-\pdfinfoomitdate=1
-\pdfsuppressptexinfo=-1
-\pdftrailerid{}
 
@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{results/signal-epilepsy}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{tmp/signal-epilepsy}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{results/cnn-epilepsy}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{tmp/cnn-epilepsy}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal-eyes-open}
+		\includegraphics[scale=0.2]{tmp/signal-eyes-open}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal-eyes-closed}
+		\includegraphics[scale=0.2]{tmp/signal-eyes-closed}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal-healthy-area}
+		\includegraphics[scale=0.2]{tmp/signal-healthy-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal-tumor-area}
+		\includegraphics[scale=0.2]{tmp/signal-tumor-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{results/signal-epilepsy}
+		\includegraphics[scale=0.2]{tmp/signal-epilepsy}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal-as-image-eyes-open}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-open}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal-as-image-eyes-closed}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-closed}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal-as-image-healthy-area}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-healthy-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal-as-image-tumor-area}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-tumor-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/signal-as-image-epilepsy}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-epilepsy}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram-eyes-open}
+		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-open}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram-eyes-closed}
+		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-closed}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram-healthy-area}
+		\includegraphics[scale=0.5]{tmp/spectrogram-healthy-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram-tumor-area}
+		\includegraphics[scale=0.5]{tmp/spectrogram-tumor-area}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/spectrogram-epilepsy}
+		\includegraphics[scale=0.5]{tmp/spectrogram-epilepsy}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn-eyes-open}
+		\includegraphics[scale=0.5]{tmp/cnn-eyes-open}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn-eyes-closed}
+		\includegraphics[scale=0.5]{tmp/cnn-eyes-closed}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn-healthy-area}
+		\includegraphics[scale=0.5]{tmp/cnn-healthy-area}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn-tumor-area}
+		\includegraphics[scale=0.5]{tmp/cnn-tumor-area}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{results/cnn-epilepsy}
+		\includegraphics[scale=0.5]{tmp/cnn-epilepsy}
 		\caption{Epilepsy}
@@
 		\centering
-		\input{results/results.tex}
+		\input{tmp/results.tex}
 	\end{minipage}
@@
 \bibliographystyle{IEEEtran}
-\bibliography{ms}
+\bibliography{ms.bib}
 

### 2020-11-30 dataset.py

@@ -7,8 +7,8 @@ from torch.utils.data import Dataset
 
 
 class UCI_epilepsy(Dataset):
-    def __init__(self, training_validation_test, num_samples, tmp_dir):
-        filename = f'{tmp_dir}/data.csv'
+    def __init__(self, training_validation_test, num_samples):
+        filename = 'tmp/data.csv'
         if not os.path.isfile(filename):
             urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
         dataset = pd.read_csv(filename)

### 2020-11-30 main.py

@@ -20,8 +20,6 @@ from utilities import save_signal, save_signal_as_image, save_spectrogram, save_
 if __name__ == '__main__':
     # DO NOT EDIT BLOCK - Required by the Makefile
     parser = argparse.ArgumentParser()
-    parser.add_argument('results_dir')
-    parser.add_argument('tmp_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
     # END OF DO NOT EDIT BLOCK
@@ -43,9 +41,9 @@ if __name__ == '__main__':
     batch_size = 20
     signals_all_max = 2047
     signals_all_min = -1885
-    training_dataset = UCI_epilepsy('training', num_samples, args.tmp_dir)
-    validation_dataset = UCI_epilepsy('validation', num_samples, args.tmp_dir)
-    test_dataset = UCI_epilepsy('test', num_samples, args.tmp_dir)
+    training_dataset = UCI_epilepsy('training', num_samples)
+    validation_dataset = UCI_epilepsy('validation', num_samples)
+    test_dataset = UCI_epilepsy('test', num_samples)
     training_dataloader = DataLoader(dataset=training_dataset, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=validation_dataset, batch_size=batch_size, shuffle=False)
     test_dataloader = DataLoader(dataset=test_dataset, batch_size=batch_size)
@@ -111,9 +109,9 @@ if __name__ == '__main__':
             results[combined_model_name]['validation_accuracy'].append(validation_accuracy)
             if validation_accuracy > best_validation_accuracy:
                 best_validation_accuracy = validation_accuracy
-                torch.save(model, f'{args.tmp_dir}/{combined_model_name}.pt')
+                torch.save(model, f'tmp/{combined_model_name}.pt')
                 print('saving as best model')
-        model = torch.load(f'{args.tmp_dir}/{combined_model_name}.pt')
+        model = torch.load(f'tmp/{combined_model_name}.pt')
         model.eval()
         test_loss_sum = 0
         corrects = 0
@@ -134,7 +132,7 @@ if __name__ == '__main__':
         results[combined_model_name]['test_accuracy'] = test_accuracy
         print(f'Model: {combined_model_name}, Epoch: {epoch}, Loss: {test_loss:.3f}, Accuracy: {test_accuracy:.2f}%')
[…]

### 2020-11-30 utilities.py

@@ -6,17 +6,17 @@ from PIL import Image
 from scipy.signal import spectrogram, resample
 
 
-def save_signal(signals_all, signal_index, label_name, results_dir):
+def save_signal(signals_all, signal_index, label_name):
     data = signals_all[signal_index].squeeze().cpu().detach().numpy()
     plt.figure()
     plt.plot(data, linewidth=4, color='k')
     plt.axis('off')
     plt.xlim([0, 177])
     plt.ylim([-1000, 1000])
-    plt.savefig(f'{results_dir}/signal-{label_name}.png')
+    plt.savefig(f'tmp/signal-{label_name}.png')
     plt.close()
 
-def save_signal_as_image(signals_all, signal_index, label_name, results_dir):
+def save_signal_as_image(signals_all, signal_index, label_name):
     signals_all_min = -1000
     signals_all_max = 1000
     x = signals_all[signal_index] - signals_all_min
@@ -26,18 +26,18 @@ def save_signal_as_image(signals_all, signal_index, label_name, results_dir):
     for index in range(178):
         data[177 - x[index], index] = 255
     plt.figure()
-    plt.imsave(f'{results_dir}/signal-as-image-{label_name}.png', data, cmap='gray')
+    plt.imsave(f'tmp/signal-as-image-{label_name}.png', data, cmap='gray')
     plt.close()
 
-def save_spectrogram(signals_all, signal_index, label_name, results_dir):
+def save_spectrogram(signals_all, signal_index, label_name):
     _, _, Sxx = spectrogram(signals_all[signal_index].cpu(), fs=178, noverlap=4, nperseg=8, nfft=64, mode='magnitude')
     data = np.array(Image.fromarray(Sxx[0, :, :]).resize((178, 178), resample=1))
     plt.figure()
-    plt.imsave(f'{results_dir}/spectrogram-{label_name}.png', data, cmap='gray')
+    plt.imsave(f'tmp/spectrogram-{label_name}.png', data, cmap='gray')
     plt.close()
 
-def save_cnn(signals_all, signal_index, label_name, results_dir, tmp_dir):
-    model = torch.load(f'{tmp_dir}/alexnet-cnn-one-layer.pt')
+def save_cnn(signals_all, signal_index, label_name):
+    model = torch.load('tmp/alexnet-cnn-one-layer.pt')
     device = next(model.parameters()).device
[…]

### 2021-01-31 main.py
getting files from urls is unreliable

@@ -4,7 +4,6 @@ import numpy as np
 import os
 import pandas as pd
 import torch
-import urllib
 
 from PIL import Image
 from matplotlib import pyplot as plt
@@ -528,10 +527,8 @@ def densenet161(num_samples):
 
 class UCI_epilepsy(Dataset):
     def __init__(self, training_validation_test, num_samples):
-        filename = 'tmp/data.csv'
-        if not os.path.isfile(filename):
-            urllib.request.urlretrieve("https://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv", filename)
-        dataset = pd.read_csv(filename)
+        # from http://web.archive.org/web/20200211041631/http://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv
+        dataset = pd.read_csv('data.csv')
         dataset = dataset[:num_samples]
         signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
         labels_all = dataset['y']
@@ -700,7 +697,7 @@ if __name__ == '__main__':
     df.columns = base_models_names
     df.to_latex('tmp/results.tex', bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
-    dataset = pd.read_csv('tmp/data.csv')
+    dataset = pd.read_csv('data.csv')
     signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
     labels_all = dataset['y']
     signals_all = torch.tensor(signals_all.values, dtype=torch.float)

### 2021-01-31 main.py
get UCI data from internet archive

@@ -4,6 +4,7 @@ import numpy as np
 import os
 import pandas as pd
 import torch
+import urllib
 
 from PIL import Image
 from matplotlib import pyplot as plt
@@ -527,8 +528,10 @@ def densenet161(num_samples):
 
 class UCI_epilepsy(Dataset):
     def __init__(self, training_validation_test, num_samples):
-        # from http://web.archive.org/web/20200211041631/http://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv
-        dataset = pd.read_csv('data.csv')
+        filename = 'tmp/data.csv'
+        if not os.path.isfile(filename):
+            urllib.request.urlretrieve('https://web.archive.org/web/20200318000445/http://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv', filename)
+        dataset = pd.read_csv(filename)
         dataset = dataset[:num_samples]
         signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
         labels_all = dataset['y']
@@ -697,7 +700,7 @@ if __name__ == '__main__':
     df.columns = base_models_names
     df.to_latex('tmp/results.tex', bold_rows=True, escape=False, column_format='l|c|c|cccc|ccccc|cccc')
 
-    dataset = pd.read_csv('data.csv')
+    dataset = pd.read_csv('tmp/data.csv')
     signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])
     labels_all = dataset['y']
     signals_all = torch.tensor(signals_all.values, dtype=torch.float)

### 2021-01-31 main.py
replace urlretrieve with requests

@@ -3,8 +3,8 @@ import collections
 import numpy as np
 import os
 import pandas as pd
+import requests
 import torch
-import urllib
 
 from PIL import Image
 from matplotlib import pyplot as plt
@@ -529,8 +529,9 @@ def densenet161(num_samples):
 class UCI_epilepsy(Dataset):
     def __init__(self, training_validation_test, num_samples):
         filename = 'tmp/data.csv'
-        if not os.path.isfile(filename):
-            urllib.request.urlretrieve('https://web.archive.org/web/20200318000445/http://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv', filename)
+        with open(filename, 'wb') as file:
+            response = requests.get('https://web.archive.org/web/20200318000445/http://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv')
+            file.write(response.content)
         dataset = pd.read_csv(filename)
         dataset = dataset[:num_samples]
         signals_all = dataset.drop(columns=['Unnamed: 0', 'y'])

### 2021-02-03 ms.tex
fix email

@@
 
-\title{\LARGE \bf Signal2Image Modules in Deep Neural Networks for EEG Classification}
+\title{Signal2Image Modules in Deep Neural Networks for EEG Classification}
 \author{Paschalis Bizopoulos, George I. Lambrou and Dimitrios Koutsouris%
-\thanks{The authors are with Biomedical Engineering Laboratory, School of Electrical and Computer Engineering, National Technical University of Athens, Athens 15780, Greece e-mail: {\tt\small pbizopoulos@biomed.ntua.gr}, {\tt\small glamprou@med.uoa.gr}, {\tt\small dkoutsou@biomed.ntua.gr.}}
+\thanks{The authors are with Biomedical Engineering Laboratory, School of Electrical and Computer Engineering, National Technical University of Athens, Athens 15780, Greece e-mail: {\tt\small pbizopoulos@protonmail.com}, {\tt\small glamprou@med.uoa.gr}, {\tt\small dkoutsou@biomed.ntua.gr.}}
 }

### 2021-09-21 ms.tex
init

@@
 \usepackage{subcaption}
+\usepackage{adjustbox}
 \usepackage{tabularx}
@@
 \renewcommand\theadfont{\bfseries}
-\IEEEoverridecommandlockouts
+\IEEEoverridecommandlockouts{}
 
@@
 
-One common approach that previous studies have used for classifying EEG signals was feature extraction from the frequency and time-frequency domains utilizing the theory behind EEG band frequencies~\cite{langkvist2012sleep}: delta (0.5-4 Hz), theta (4-8 Hz), alpha (8-13 Hz), beta (13-20 Hz) and gamma (20-64 Hz).
+One common approach that previous studies have used for classifying EEG signals was feature extraction from the frequency and time-frequency domains utilizing the theory behind EEG band frequencies~\cite{langkvist2012sleep}: delta (0.5--4 Hz), theta (4--8 Hz), alpha (8--13 Hz), beta (13--20 Hz) and gamma (20--64 Hz).
 Truong et al.~\cite{truong2018convolutional} used Short-Time Fourier Transform (STFT) on a 30 second sliding window to train a three layer CNN on stacked time-frequency representations for seizure prediction and evaluated their method on three EEG databases.
@@
 The UCI EEG epileptic seizure recognition dataset~\cite{andrzejak2001indications} consists of $500$ signals each one with $4097$ samples (23.5 seconds).
-The dataset is annotated into five classes with $100$ signals for each class (in parenthesis the shortened label names used in Fig. \ref{fig:highleveloverview} and \ref{fig:signal2imageoutputs}):
+The dataset is annotated into five classes with $100$ signals for each class (in parenthesis the shortened label names used in Fig.~\ref{fig:highleveloverview} and~\ref{fig:signal2imageoutputs}):
 \begin{enumerate}
@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{tmp/signal-epilepsy}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{tmp/signal-epilepsy.png}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{tmp/cnn-epilepsy}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{tmp/cnn-epilepsy.png}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 	Arrows denote the flow of the feed-forward pass.
-	For the 1D architectures $m$ is omitted and no intermediate image is generated.}
-	\label{fig:highleveloverview}
+	For the 1D architectures $m$ is omitted and no intermediate image is generated.}\label{fig:highleveloverview}
 \end{figure}
@@
 \subsection{Definitions}
-We define the dataset $D=\{x_i, y_i\}_{i=1...N}$ where $x_i \in \mathbb{Z}^n$ and $y_i \in \{1, 2, 3, 4, 5\}$ denote the $i^{th}$ input signal with dimensionality $n=178$ and the $i^{th}$ label with five possible classes respectively.
+We define the dataset $D=\{x_i, y_i\}_{i=1\ldots N}$ where $x_i \in \mathbb{Z}^n$ and $y_i \in \{1, 2, 3, 4, 5\}$ denote the $i^{th}$ input signal with dimensionality $n=178$ and the $i^{th}$ label with five possible classes respectively.
 $N=11500$ is the number of observations.
@@
 Using the previous definitions, the aim of this paper is the evaluation of the set of models $C$, where $C$ is the combined set of $M$ and $B$ i.e.
-$C=M\times B$ w.r.t.
-time performance and class accuracy trained on $D$.
+$C=M\times B$ w.r.t.\ time performance and class accuracy trained on $D$.
 
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-eyes-open}
+		\includegraphics[scale=0.2]{tmp/signal-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-eyes-closed}
+		\includegraphics[scale=0.2]{tmp/signal-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-healthy-area}
+		\includegraphics[scale=0.2]{tmp/signal-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-tumor-area}
+		\includegraphics[scale=0.2]{tmp/signal-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-epilepsy}
+		\includegraphics[scale=0.2]{tmp/signal-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-open}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-closed}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-healthy-area}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-tumor-area}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-epilepsy}
+		\includegraphics[scale=0.5]{tmp/signal-as-image-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-open}
+		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-closed}
+		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-healthy-area}
+		\includegraphics[scale=0.5]{tmp/spectrogram-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-tumor-area}
+		\includegraphics[scale=0.5]{tmp/spectrogram-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-epilepsy}
+		\includegraphics[scale=0.5]{tmp/spectrogram-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-eyes-open}
+		\includegraphics[scale=0.5]{tmp/cnn-eyes-open.png}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-eyes-closed}
+		\includegraphics[scale=0.5]{tmp/cnn-eyes-closed.png}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-healthy-area}
+		\includegraphics[scale=0.5]{tmp/cnn-healthy-area.png}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-tumor-area}
+		\includegraphics[scale=0.5]{tmp/cnn-tumor-area.png}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-epilepsy}
+		\includegraphics[scale=0.5]{tmp/cnn-epilepsy.png}
 		\caption{Epilepsy}
@@
 	\caption{Visualizations of the original signals and the outputs of the S2Is for each class.
-	The x, y-axis of the first row are in \SI{}{\micro V} and time samples respectively.
+	The x, y-axis of the first row are in \SI{}{\micro{} V} and time samples respectively.
 	The x, y-axis of the rest of the subfigures denote spatial information, since we do not inform the `base model' the concept of time along the x-axis or the concept of frequency along the y-axis.
-	Higher pixel intensity denotes higher amplitude.}
-	\label{fig:signal2imageoutputs}
+	Higher pixel intensity denotes higher amplitude.}\label{fig:signal2imageoutputs}
 \end{figure*}
@@
 All networks were trained for $100$ epochs and model selection was performed using the best validation accuracy out of all the epochs.
-We used PyTorch~\cite{paszke2017automatic} for implementing the neural network architectures and training/preprocessing was done using a NVIDIA Titan X Pascal GPU 12GB RAM and a 12 Core Intel i7-8700 CPU @ 3.20GHz on a Linux operating system.
+We used PyTorch~\cite{paszke2017automatic} for implementing the neural network architectures and training/preprocessing was done using a NVIDIA Titan X Pascal GPU 12GB RAM and a 12 Core Intel i7--8700 CPU @ 3.20GHz on a Linux operating system.
 
@@
 	The second row indicates the number of layers.
-	Bold indicates the best accuracy for each base model.}
-	\label{table:results}
-	\begin{minipage}{\textwidth}
-		\setlength\tabcolsep{0.6pt}
-		\centering
+	Bold indicates the best accuracy for each base model.}\label{table:results}
+	\begin{adjustbox}{width=\textwidth}
 		\input{tmp/results.tex}
-	\end{minipage}
+	\end{adjustbox}
 \end{table*}

### 2021-09-21 main.py

@@ -1,0 +1,690 @@
+import collections
+import os
+
+import numpy as np
+import pandas as pd
+import requests
+import torch
+from matplotlib import pyplot as plt
+from PIL import Image
+from scipy.signal import spectrogram
+from torch import nn
+from torch.nn import functional as F
+from torch.optim import Adam
+from torch.utils.data import DataLoader, Dataset
+from torchvision import models
+
+tmpdir = os.getenv('TMPDIR')
+full = os.getenv('FULL')
+
+
+def save_signal(signals_all, signal_index, label_name):
+    plt.figure()
+    plt.plot(signals_all[signal_index].squeeze(), linewidth=4, color='k')
+    plt.axis('off')
+    plt.xlim([0, signals_all.shape[-1] - 1])
+    plt.ylim([-1000, 1000])
+    plt.savefig(f'{tmpdir}/signal-{label_name}.png')
+    plt.close()
+
+
+def save_signal_as_image(signals_all, signal_index, label_name):
+    signals_all_min = -1000
+    signals_all_max = 1000
+    x = signals_all[signal_index] - signals_all_min
+    x = signals_all.shape[-1] * x / (signals_all_max - signals_all_min)
+    x = x.squeeze(0).floor().long()
+    data = torch.zeros(signals_all.shape[-1], signals_all.shape[-1])
+    for index in range(signals_all.shape[-1]):
+        data[signals_all.shape[-1] - 1 - x[index], index] = 255
+    plt.figure()
+    plt.imsave(f'{tmpdir}/signal-as-image-{label_name}.png', data, cmap='gray')
+    plt.close()
+
+
+def save_spectrogram(signals_all, signal_index, label_name):
+    _, _, Sxx = spectrogram(signals_all[signal_index], fs=signals_all.shape[-1], noverlap=4, nperseg=8, nfft=64, mode='magnitude')
+    data = np.array(Image.fromarray(Sxx[0]).resize((signals_all.shape[-1], signals_all.shape[-1]), resample=1))
+    plt.figure()
+    plt.imsave(f'{tmpdir}/spectrogram-{label_name}.png', data, cmap='gray')
+    plt.close()
+
+
+def save_cnn(signals_all, signal_index, label_name):
+    model = torch.load(f'{tmpdir}/alexnet-cnn-one-layer.pt')
+    device = next(model.parameters()).device
+    signal = signals_all[signal_index].unsqueeze(0).to(device)
+    outputs = []
+
+    def hook(_, __, output):
+        outputs.append(output)
+
[…]

### 2022-03-21 ms.tex
Makefile major change

@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{tmp/signal-epilepsy.png}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{artifacts/signal-epilepsy.png}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{tmp/cnn-epilepsy.png}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{artifacts/cnn-epilepsy.png}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-eyes-open.png}
+		\includegraphics[scale=0.2]{artifacts/signal-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-eyes-closed.png}
+		\includegraphics[scale=0.2]{artifacts/signal-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-healthy-area.png}
+		\includegraphics[scale=0.2]{artifacts/signal-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-tumor-area.png}
+		\includegraphics[scale=0.2]{artifacts/signal-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{tmp/signal-epilepsy.png}
+		\includegraphics[scale=0.2]{artifacts/signal-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-open.png}
+		\includegraphics[scale=0.5]{artifacts/signal-as-image-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-eyes-closed.png}
+		\includegraphics[scale=0.5]{artifacts/signal-as-image-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-healthy-area.png}
+		\includegraphics[scale=0.5]{artifacts/signal-as-image-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-tumor-area.png}
+		\includegraphics[scale=0.5]{artifacts/signal-as-image-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/signal-as-image-epilepsy.png}
+		\includegraphics[scale=0.5]{artifacts/signal-as-image-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-open.png}
+		\includegraphics[scale=0.5]{artifacts/spectrogram-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-eyes-closed.png}
+		\includegraphics[scale=0.5]{artifacts/spectrogram-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-healthy-area.png}
+		\includegraphics[scale=0.5]{artifacts/spectrogram-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-tumor-area.png}
+		\includegraphics[scale=0.5]{artifacts/spectrogram-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/spectrogram-epilepsy.png}
+		\includegraphics[scale=0.5]{artifacts/spectrogram-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-eyes-open.png}
+		\includegraphics[scale=0.5]{artifacts/cnn-eyes-open.png}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-eyes-closed.png}
+		\includegraphics[scale=0.5]{artifacts/cnn-eyes-closed.png}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-healthy-area.png}
+		\includegraphics[scale=0.5]{artifacts/cnn-healthy-area.png}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-tumor-area.png}
+		\includegraphics[scale=0.5]{artifacts/cnn-tumor-area.png}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{tmp/cnn-epilepsy.png}
+		\includegraphics[scale=0.5]{artifacts/cnn-epilepsy.png}
 		\caption{Epilepsy}
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{tmp/results.tex}
+		\input{artifacts/results.tex}
 	\end{adjustbox}

### 2022-03-21 main.py

@@ -1,4 +1,5 @@
 import os
+from os.path import join
 from shutil import rmtree
 
 import numpy as np
@@ -17,21 +18,21 @@ from torch.optim import Adam
 from torch.utils.data import DataLoader, Dataset
 from torchvision import models
 
-tmpdir = os.getenv('TMPDIR')
+artifacts_dir = os.getenv('ARTIFACTSDIR')
 full = os.getenv('FULL')
 
 
 def save_tfjs_from_torch(model, model_name, input_shape):
-    model_name_dir = f'{tmpdir}/tfjs-models/{model_name}'
+    model_name_dir = join(artifacts_dir, 'tfjs-models', model_name)
     os.makedirs(model_name_dir, exist_ok=True)
     example_input = torch.randn(*input_shape, requires_grad=False)
-    torch.onnx.export(model.cpu(), example_input, f'{model_name_dir}/model.onnx', export_params=True, opset_version=11)
-    onnx_model = onnx.load(f'{model_name_dir}/model.onnx')
+    torch.onnx.export(model.cpu(), example_input, join(model_name_dir, 'model.onnx'), export_params=True, opset_version=11)
+    onnx_model = onnx.load(join(model_name_dir, 'model.onnx'))
     tf_model = prepare(onnx_model)
-    tf_model.export_graph(f'{model_name_dir}/model')
-    tf_saved_model_conversion_v2.convert_tf_saved_model(f'{model_name_dir}/model', model_name_dir, skip_op_check=True)
-    rmtree(f'{model_name_dir}/model')
-    os.remove(f'{model_name_dir}/model.onnx')
+    tf_model.export_graph(join(model_name_dir, 'model'))
+    tf_saved_model_conversion_v2.convert_tf_saved_model(join(model_name_dir, 'model'), model_name_dir, skip_op_check=True)
+    rmtree(join(model_name_dir, 'model'))
+    os.remove(join(model_name_dir, 'model.onnx'))
 
 
 def save_figure_signal(signals_all, signal_index, label_name):
@@ -40,7 +41,7 @@ def save_figure_signal(signals_all, signal_index, label_name):
     plt.axis('off')
     plt.xlim([0, signals_all.shape[-1] - 1])
     plt.ylim([-1000, 1000])
-    plt.savefig(f'{tmpdir}/signal-{label_name}.png')
+    plt.savefig(join(artifacts_dir, f'signal-{label_name}.png'))
     plt.close()
 
 
[…]

### 2022-04-21 ms.tex
fix names

@@
 The UCI EEG epileptic seizure recognition dataset~\cite{andrzejak2001indications} consists of $500$ signals each one with $4097$ samples (23.5 seconds).
-The dataset is annotated into five classes with $100$ signals for each class (in parenthesis the shortened label names used in Fig.~\ref{fig:highleveloverview} and~\ref{fig:signal2imageoutputs}):
+The dataset is annotated into five classes with $100$ signals for each class (in parenthesis the shortened class names used in Fig.~\ref{fig:highleveloverview} and~\ref{fig:signal2imageoutputs}):
 \begin{enumerate}
@@
 	$x_i$ is the input, $m$ is the Signal2Image module, $b_{d}$ is the 1D or 2D architecture `base model' for $d=1,2$ respectively and $\hat{y_i}$ is the predicted output.
-	The names of the labels are depicted at the right along with the predictions for this example signal.
+	The names of the classes are depicted at the right along with the predictions for this example signal.
 	The image between $m$ and $b_{d}$ depicts the output of the one layer CNN Signal2Image module, while the `signal as image' and spectrogram have intermediate images as those depicted at the second and third row of Fig.~\ref{fig:signal2imageoutputs}.
@@
 \subsection{Definitions}
-We define the dataset $D=\{x_i, y_i\}_{i=1\ldots N}$ where $x_i \in \mathbb{Z}^n$ and $y_i \in \{1, 2, 3, 4, 5\}$ denote the $i^{th}$ input signal with dimensionality $n=178$ and the $i^{th}$ label with five possible classes respectively.
+We define the dataset $D=\{x_i, y_i\}_{i=1\ldots N}$ where $x_i \in \mathbb{Z}^n$ and $y_i \in \{1, 2, 3, 4, 5\}$ denote the $i^{th}$ input signal with dimensionality $n=178$ and the $i^{th}$ class with five possible classes respectively.
 $N=11500$ is the number of observations.

### 2022-04-21 main.py

@@ -27,34 +27,34 @@ class Hook:
         self.outputs.append(module_out)
 
 
-def replace_last_layer(model_base, model_full_name, num_classes):
-    if model_full_name.startswith(('alexnet', 'vgg')):
-        model_base.classifier[-1] = nn.Linear(model_base.classifier[-1].in_features, num_classes)
-    elif model_full_name.startswith('resnet'):
-        model_base.fc = nn.Linear(model_base.fc.in_features, num_classes)
-    elif model_full_name.startswith('densenet'):
-        model_base.classifier = nn.Linear(model_base.classifier.in_features, num_classes)
+def replace_last_layer(model_base, model_file_name, classes_num):
+    if model_file_name.startswith(('alexnet', 'vgg')):
+        model_base.classifier[-1] = nn.Linear(model_base.classifier[-1].in_features, classes_num)
+    elif model_file_name.startswith('resnet'):
+        model_base.fc = nn.Linear(model_base.fc.in_features, classes_num)
+    elif model_file_name.startswith('densenet'):
+        model_base.classifier = nn.Linear(model_base.classifier.in_features, classes_num)
     return model_base
 
 
 def save_tfjs_from_torch(artifacts_dir, example_input, model, model_name):
-    model_name_dir = join(artifacts_dir, 'tfjs-models', model_name)
-    os.makedirs(model_name_dir, exist_ok=True)
-    torch.onnx.export(model.cpu(), example_input, join(model_name_dir, 'model.onnx'), export_params=True, opset_version=11)
-    onnx_model = onnx.load(join(model_name_dir, 'model.onnx'))
-    tf_model = prepare(onnx_model)
-    tf_model.export_graph(join(model_name_dir, 'model'))
-    tf_saved_model_conversion_v2.convert_tf_saved_model(join(model_name_dir, 'model'), model_name_dir, skip_op_check=True)
-    rmtree(join(model_name_dir, 'model'))
-    os.remove(join(model_name_dir, 'model.onnx'))
+    model_file_path = join(artifacts_dir, 'tfjs-models', model_name)
+    os.makedirs(model_file_path, exist_ok=True)
+    torch.onnx.export(model.cpu(), example_input, join(model_file_path, 'model.onnx'), export_params=True, opset_version=11)
[…]

### 2022-05-16 python/main.py
major changes

@@ -1,6 +1,7 @@
 from PIL import Image
 from matplotlib import pyplot as plt
 from onnx_tf.backend import prepare
+from os import environ
 from os.path import join
 from scipy.signal import spectrogram
 from shutil import rmtree
@@ -417,8 +418,8 @@ def densenet201(samples_num):
 
 
 def main():
-    artifacts_dir = os.getenv('ARTIFACTSDIR')
-    full = os.getenv('FULL')
+    artifacts_dir = environ['ARTIFACTSDIR']
+    full = environ['FULL']
     samples_num = 11500
     epochs_num = 100
     if not full:

### 2022-05-16 script.js

@@ -4,7 +4,7 @@ const canvasHeight = 256;
 const canvasWidth = 256;
 const classNames = ['Open', 'Closed', 'Healthy', 'Tumor', 'Epilepsy'];
 const inputDiv = document.getElementById('inputDiv');
-const inputFileName = 'https://raw.githubusercontent.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/main/docs/eeg-classification-example-data.txt';
+const inputFileName = 'python/release/eeg-classification-example-data.txt';
 const signalFileReader = new FileReader();
 let csvDataset;
 let csvDatasetMax;
@@ -39,7 +39,7 @@ function drawSignal(text) {
 
 async function loadModel(predictFunction) {
 	const loadModelFunction = tf.loadGraphModel;
-	model = await loadModelFunction('https://raw.githubusercontent.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/main/docs/resnet34-1D/model.json', {
+	model = await loadModelFunction('python/release/resnet34-1D/model.json', {
 		onProgress: function (fraction) {
 			document.getElementById('modelDownloadFractionDiv').textContent = `Downloading model, please wait ${Math.round(100*fraction)}%.`;
 			if (fraction == 1) {

### 2022-05-17 python/main.py
apply source_normalizer

@@ -4,7 +4,7 @@ from onnx_tf.backend import prepare
 from os import environ
 from os.path import join
 from scipy.signal import spectrogram
-from shutil import rmtree
+from shutil import move, rmtree
 from tensorflowjs.converters import tf_saved_model_conversion_v2
 from torch import nn
 from torch.nn import functional as F
@@ -21,7 +21,7 @@ import torch
 
 class BasicBlock(nn.Module):
 
-    def __init__(self, inplanes, planes, stride=1, downsample=None):
+    def __init__(self, downsample, inplanes, planes, stride=1):
         super().__init__()
         self.conv1 = conv3x3(inplanes, planes, stride)
         self.bn1 = nn.BatchNorm1d(planes)
@@ -47,7 +47,7 @@ class BasicBlock(nn.Module):
 
 class Bottleneck(nn.Module):
 
-    def __init__(self, inplanes, planes, stride=1, downsample=None):
+    def __init__(self, downsample, inplanes, planes, stride=1):
         super().__init__()
         expansion = 4
         self.conv1 = conv1x1(inplanes, planes)
@@ -204,10 +204,10 @@ class ResNet(nn.Module):
         if stride != 1 or self.inplanes != planes * expansion:
             downsample = nn.Sequential(conv1x1(self.inplanes, planes * expansion, stride), nn.BatchNorm1d(planes * expansion))
         layers = []
-        layers.append(block(self.inplanes, planes, stride, downsample))
+        layers.append(block(downsample, self.inplanes, planes, stride))
         self.inplanes = planes * expansion
         for _ in range(1, blocks):
-            layers.append(block(self.inplanes, planes))
+            layers.append(block(None, self.inplanes, planes))
         return nn.Sequential(*layers)
 
     def forward(self, x):
@@ -502,10 +502,11 @@ def main():
             test_accuracy = 100 * corrects / (batch_size * len(test_dataloader))
             test_loss = test_loss_sum / (batch_size * len(test_dataloader))
             test_accuracy_array[model_module_name_index, model_base_name_index] = test_accuracy
-            if model_file_name in ['lenet-1D', 'alexnet-1D', 'resnet18-1D', 'resnet34-1D', 'resnet50-1D', 'resnet18-signal-as-image', 'resnet34-signal-as-image', 'resnet50-signal-as-image']:
+            if model_file_name == 'resnet34-1D':
[…]

### 2022-07-07 ms.tex
major changes
init

@@
 \documentclass[conference]{IEEEtran}
+\usepackage[nopdftrailerid=true]{pdfprivacy}
 \usepackage{multirow}
@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{artifacts/signal-epilepsy.png}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{python/artifacts/signal-epilepsy.png}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{artifacts/cnn-epilepsy.png}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{python/artifacts/cnn-epilepsy.png}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-eyes-open.png}
+		\includegraphics[scale=0.2]{python/artifacts/signal-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-eyes-closed.png}
+		\includegraphics[scale=0.2]{python/artifacts/signal-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-healthy-area.png}
+		\includegraphics[scale=0.2]{python/artifacts/signal-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-tumor-area.png}
+		\includegraphics[scale=0.2]{python/artifacts/signal-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-epilepsy.png}
+		\includegraphics[scale=0.2]{python/artifacts/signal-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-eyes-open.png}
+		\includegraphics[scale=0.5]{python/artifacts/signal-as-image-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/artifacts/signal-as-image-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-healthy-area.png}
+		\includegraphics[scale=0.5]{python/artifacts/signal-as-image-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-tumor-area.png}
+		\includegraphics[scale=0.5]{python/artifacts/signal-as-image-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-epilepsy.png}
+		\includegraphics[scale=0.5]{python/artifacts/signal-as-image-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-eyes-open.png}
+		\includegraphics[scale=0.5]{python/artifacts/spectrogram-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/artifacts/spectrogram-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-healthy-area.png}
+		\includegraphics[scale=0.5]{python/artifacts/spectrogram-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-tumor-area.png}
+		\includegraphics[scale=0.5]{python/artifacts/spectrogram-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-epilepsy.png}
+		\includegraphics[scale=0.5]{python/artifacts/spectrogram-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-eyes-open.png}
+		\includegraphics[scale=0.5]{python/artifacts/cnn-eyes-open.png}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/artifacts/cnn-eyes-closed.png}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-healthy-area.png}
+		\includegraphics[scale=0.5]{python/artifacts/cnn-healthy-area.png}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-tumor-area.png}
+		\includegraphics[scale=0.5]{python/artifacts/cnn-tumor-area.png}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-epilepsy.png}
+		\includegraphics[scale=0.5]{python/artifacts/cnn-epilepsy.png}
 		\caption{Epilepsy}
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{artifacts/results.tex}
+		\input{python/artifacts/results.tex}
 	\end{adjustbox}

### 2022-07-07 python/main.py

@@ -1,0 +1,645 @@
+from PIL import Image
+from matplotlib import pyplot as plt
+from onnx_tf.backend import prepare
+from os import environ
+from os.path import join
+from scipy.signal import spectrogram
+from shutil import move, rmtree
+from tensorflowjs.converters import tf_saved_model_conversion_v2
+from torch import nn
+from torch.nn import functional
+from torch.optim import Adam
+from torch.utils.data import DataLoader, Dataset
+from torchvision import models
+import numpy as np
+import onnx
+import os
+import pandas as pd
+import requests
+import torch
+
+
+class Alexnet(nn.Module):
+
+    def __init__(self, classes_num):
+        super().__init__()
+        self.features = nn.Sequential(nn.Conv1d(1, 64, kernel_size=11, stride=4, padding=2), nn.ReLU(inplace=True), nn.MaxPool1d(kernel_size=3, stride=2), nn.Conv1d(64, 192, kernel_size=5, padding=2), nn.ReLU(inplace=True), nn.MaxPool1d(kernel_size=3, stride=2), nn.Conv1d(192, 384, kernel_size=3, padding=1), nn.ReLU(inplace=True), nn.Conv1d(384, 256, kernel_size=3, padding=1), nn.ReLU(inplace=True), nn.Conv1d(256, 256, kernel_size=3, padding=1), nn.ReLU(inplace=True), nn.MaxPool1d(kernel_size=3, stride=2))
+        self.classifier = nn.Sequential(nn.Dropout(), nn.Linear(256 * 4, 4096), nn.ReLU(inplace=True), nn.Dropout(), nn.Linear(4096, 4096), nn.ReLU(inplace=True), nn.Linear(4096, classes_num))
+
+    def forward(self, signal):
+        out = self.features(signal)
+        out = out.view(out.size(0), 256 * 4)
+        out = self.classifier(out)
+        return out
+
+
+class BasicBlock(nn.Module):
+
+    def __init__(self, downsample, inplanes, planes, stride=1):
+        super().__init__()
+        self.conv1 = conv3x3(inplanes, planes, stride)
+        self.bn1 = nn.BatchNorm1d(planes)
+        self.relu = nn.ReLU(inplace=True)
+        self.conv2 = conv3x3(planes, planes)
+        self.bn2 = nn.BatchNorm1d(planes)
+        self.downsample = downsample
+        self.stride = stride
+
+    def forward(self, signal):
+        identity = signal
+        out = self.conv1(signal)
[…]

### 2022-10-06 ms.tex
fix

--- 2022-04-21 ms.tex
@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{artifacts/signal-epilepsy.png}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{python/bin/signal-epilepsy.png}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{artifacts/cnn-epilepsy.png}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{python/bin/cnn-epilepsy.png}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-eyes-open.png}
+		\includegraphics[scale=0.2]{python/bin/signal-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-eyes-closed.png}
+		\includegraphics[scale=0.2]{python/bin/signal-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-healthy-area.png}
+		\includegraphics[scale=0.2]{python/bin/signal-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-tumor-area.png}
+		\includegraphics[scale=0.2]{python/bin/signal-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{artifacts/signal-epilepsy.png}
+		\includegraphics[scale=0.2]{python/bin/signal-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-eyes-open.png}
+		\includegraphics[scale=0.5]{python/bin/signal-as-image-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/bin/signal-as-image-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-healthy-area.png}
+		\includegraphics[scale=0.5]{python/bin/signal-as-image-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-tumor-area.png}
+		\includegraphics[scale=0.5]{python/bin/signal-as-image-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/signal-as-image-epilepsy.png}
+		\includegraphics[scale=0.5]{python/bin/signal-as-image-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-eyes-open.png}
+		\includegraphics[scale=0.5]{python/bin/spectrogram-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/bin/spectrogram-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-healthy-area.png}
+		\includegraphics[scale=0.5]{python/bin/spectrogram-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-tumor-area.png}
+		\includegraphics[scale=0.5]{python/bin/spectrogram-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/spectrogram-epilepsy.png}
+		\includegraphics[scale=0.5]{python/bin/spectrogram-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-eyes-open.png}
+		\includegraphics[scale=0.5]{python/bin/cnn-eyes-open.png}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/bin/cnn-eyes-closed.png}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-healthy-area.png}
+		\includegraphics[scale=0.5]{python/bin/cnn-healthy-area.png}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-tumor-area.png}
+		\includegraphics[scale=0.5]{python/bin/cnn-tumor-area.png}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{artifacts/cnn-epilepsy.png}
+		\includegraphics[scale=0.5]{python/bin/cnn-epilepsy.png}
 		\caption{Epilepsy}
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{artifacts/results.tex}
+		\input{python/bin/results.tex}
 	\end{adjustbox}

### 2022-10-06 python/main.py

@@ -364,8 +364,8 @@ class UCIEpilepsy(Dataset):
     def __getitem__(self, index):
         return (self.data[index], self.target[index])
 
-    def __init__(self, artifacts_dir, samples_num, training_validation_test):
-        data_file_path = join(artifacts_dir, 'data.csv')
+    def __init__(self, samples_num, training_validation_test):
+        data_file_path = join('bin', 'data.csv')
         if not os.path.isfile(data_file_path):
             with open(data_file_path, 'wb') as file:
                 response = requests.get('https://web.archive.org/web/20200318000445/http://archive.ics.uci.edu/ml/machine-learning-databases/00388/data.csv')
@@ -445,7 +445,6 @@ def densenet201(classes_num):
 
 
 def main():
-    artifacts_dir = environ['ARTIFACTS_DIR']
     full = environ['FULL']
     samples_num = 11500
     epochs_num = 100
@@ -461,9 +460,9 @@ def main():
     batch_size = 20
     signals_all_max = 2047
     signals_all_min = -1885
-    dataset_training = UCIEpilepsy(artifacts_dir, samples_num, 'training')
-    dataset_validation = UCIEpilepsy(artifacts_dir, samples_num, 'validation')
-    dataset_test = UCIEpilepsy(artifacts_dir, samples_num, 'test')
+    dataset_training = UCIEpilepsy(samples_num, 'training')
+    dataset_validation = UCIEpilepsy(samples_num, 'validation')
+    dataset_test = UCIEpilepsy(samples_num, 'test')
     dataloader_training = DataLoader(dataset=dataset_training, batch_size=batch_size, shuffle=True)
     validation_dataloader = DataLoader(dataset=dataset_validation, batch_size=batch_size)
     dataloader_test = DataLoader(dataset=dataset_test, batch_size=batch_size)
@@ -516,8 +515,8 @@ def main():
                 loss_validation = loss_validation_sum / predictions_num
                 if accuracy_validation > accuracy_validation_best:
                     accuracy_validation_best = accuracy_validation
-                    torch.save(model.state_dict(), join(artifacts_dir, f'{model_file_name}.pt'))
-            model.load_state_dict(torch.load(join(artifacts_dir, f'{model_file_name}.pt')))
+                    torch.save(model.state_dict(), join('bin', f'{model_file_name}.pt'))
[…]

### 2022-10-06 script.js

@@ -4,7 +4,7 @@ const canvasHeight = 256;
 const canvasWidth = 256;
 const classNames = ['Open', 'Closed', 'Healthy', 'Tumor', 'Epilepsy'];
 const inputDiv = document.getElementById('inputDiv');
-const inputFileName = 'python/release/eeg-classification-example-data.txt';
+const inputFileName = 'python/dist/eeg-classification-example-data.txt';
 const signalFileReader = new FileReader();
 let csvDataset;
 let csvDatasetMax;
@@ -39,7 +39,7 @@ function drawSignal(text) {
 
 async function loadModel(predictFunction) {
 	const loadModelFunction = tf.loadGraphModel;
-	model = await loadModelFunction('python/release/resnet34-1D/model.json', {
+	model = await loadModelFunction('python/dist/resnet34-1D/model.json', {
 		onProgress: function (fraction) {
 			document.getElementById('modelDownloadFractionDiv').textContent = `Downloading model, please wait ${Math.round(100*fraction)}%.`;
 			if (fraction == 1) {

### 2023-06-25 latex/python/main.py
.

@@ -544,7 +544,7 @@ class UCIEpilepsy(Dataset[tuple[torch.Tensor, torch.Tensor]]):
         samples_num: int,
         train_validation_test: str,
     ) -> None:
-        data_file_path = Path("data/data.csv")
+        data_file_path = Path("bin/data.csv")
         if not data_file_path.is_file():
             with data_file_path.open("wb") as file:
                 response = requests.get(
@@ -789,12 +789,6 @@ def vgg19(classes_num: int) -> nn.Module:
 
 
 def main() -> None:  # noqa: C901, PLR0912, PLR0915
-    bin_file_path = Path("bin")
-    if not bin_file_path.exists():
-        bin_file_path.mkdir(parents=True)
-    data_file_path = Path("data")
-    if not data_file_path.exists():
-        data_file_path.mkdir(parents=True)
     samples_num = 11500
     epochs_num = 100
     if environ["DEBUG"] == "1":
@@ -985,7 +979,7 @@ def main() -> None:  # noqa: C901, PLR0912, PLR0915
     styler.format(precision=1)
     styler.highlight_max(props="bfseries: ;")
     styler.to_latex("bin/results.tex", hrules=True)
-    dataset = pd.read_csv("data/data.csv")
+    dataset = pd.read_csv("bin/data.csv")
     signals_all = dataset.drop(columns=["Unnamed: 0", "y"])
     classes_all = dataset["y"]
     signals_all = torch.tensor(signals_all.to_numpy(), dtype=torch.float)

### 2023-06-27 latex/python/main.py
rename bin to tmp

@@ -544,7 +544,7 @@ class UCIEpilepsy(Dataset[tuple[torch.Tensor, torch.Tensor]]):
         samples_num: int,
         train_validation_test: str,
     ) -> None:
-        data_file_path = Path("bin/data.csv")
+        data_file_path = Path("tmp/data.csv")
         if not data_file_path.is_file():
             with data_file_path.open("wb") as file:
                 response = requests.get(
@@ -705,7 +705,7 @@ def save_tfjs_from_torch(
     model: nn.Module,
     model_file_name: str,
 ) -> None:
-    model_file_path = Path("bin") / model_file_name
+    model_file_path = Path("tmp") / model_file_name
     if model_file_path.exists():
         rmtree(model_file_path)
     model_file_path.mkdir()
@@ -931,7 +931,7 @@ def main() -> None:  # noqa: C901, PLR0912, PLR0915
                 accuracy_validation = 100 * predictions_correct_num / predictions_num
                 if accuracy_validation > accuracy_validation_best:
                     accuracy_validation_best = accuracy_validation
-                    model_file_path = Path(f"bin/{model_file_name}.pt")
+                    model_file_path = Path(f"tmp/{model_file_name}.pt")
                     torch.save(model.state_dict(), model_file_path)
             model.load_state_dict(torch.load(model_file_path))
             loss_test_sum = 0
@@ -962,9 +962,9 @@ def main() -> None:  # noqa: C901, PLR0912, PLR0915
                 if environ["DEBUG"] != "1":
                     dist_model_file_path = Path("dist") / model_file_name
                     rmtree(dist_model_file_path)
-                    move(Path("bin") / model_file_name, Path("dist") / model_file_name)
+                    move(Path("tmp") / model_file_name, Path("dist") / model_file_name)
             if environ["DEBUG"] == "1" and model_file_name != "alexnet-cnn-one-layer":
-                Path(f"bin/{model_file_name}.pt").unlink()
+                Path(f"tmp/{model_file_name}.pt").unlink()
     styler = pd.DataFrame(
         accuracy_test_array,
         index=[
@@ -978,8 +978,8 @@ def main() -> None:  # noqa: C901, PLR0912, PLR0915
     ).style
     styler.format(precision=1)
[…]

### 2023-06-27 latex/ms.tex
.

--- 2022-10-06 ms.tex
@@
 	\begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{python/bin/signal-epilepsy.png}};
+		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{python/tmp/signal-epilepsy.png}};
 		\node[align=left] at (-4.2, 0) {$x_i$};
@@
 		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{python/bin/cnn-epilepsy.png}};
+		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{python/tmp/cnn-epilepsy.png}};
 		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
 We define the dataset $D=\{x_i, y_i\}_{i=1\ldots N}$ where $x_i \in \mathbb{Z}^n$ and $y_i \in \{1, 2, 3, 4, 5\}$ denote the $i^{th}$ input signal with dimensionality $n=178$ and the $i^{th}$ class with five possible classes respectively.
+% chktex 3
 $N=11500$ is the number of observations.
@@
 		\centering
-		\includegraphics[scale=0.2]{python/bin/signal-eyes-open.png}
+		\includegraphics[scale=0.2]{python/tmp/signal-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{python/bin/signal-eyes-closed.png}
+		\includegraphics[scale=0.2]{python/tmp/signal-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{python/bin/signal-healthy-area.png}
+		\includegraphics[scale=0.2]{python/tmp/signal-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{python/bin/signal-tumor-area.png}
+		\includegraphics[scale=0.2]{python/tmp/signal-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.2]{python/bin/signal-epilepsy.png}
+		\includegraphics[scale=0.2]{python/tmp/signal-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/signal-as-image-eyes-open.png}
+		\includegraphics[scale=0.5]{python/tmp/signal-as-image-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/signal-as-image-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/tmp/signal-as-image-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/signal-as-image-healthy-area.png}
+		\includegraphics[scale=0.5]{python/tmp/signal-as-image-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/signal-as-image-tumor-area.png}
+		\includegraphics[scale=0.5]{python/tmp/signal-as-image-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/signal-as-image-epilepsy.png}
+		\includegraphics[scale=0.5]{python/tmp/signal-as-image-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/spectrogram-eyes-open.png}
+		\includegraphics[scale=0.5]{python/tmp/spectrogram-eyes-open.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/spectrogram-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/tmp/spectrogram-eyes-closed.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/spectrogram-healthy-area.png}
+		\includegraphics[scale=0.5]{python/tmp/spectrogram-healthy-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/spectrogram-tumor-area.png}
+		\includegraphics[scale=0.5]{python/tmp/spectrogram-tumor-area.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/spectrogram-epilepsy.png}
+		\includegraphics[scale=0.5]{python/tmp/spectrogram-epilepsy.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/cnn-eyes-open.png}
+		\includegraphics[scale=0.5]{python/tmp/cnn-eyes-open.png}
 		\caption{Open}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/cnn-eyes-closed.png}
+		\includegraphics[scale=0.5]{python/tmp/cnn-eyes-closed.png}
 		\caption{Closed}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/cnn-healthy-area.png}
+		\includegraphics[scale=0.5]{python/tmp/cnn-healthy-area.png}
 		\caption{Healthy}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/cnn-tumor-area.png}
+		\includegraphics[scale=0.5]{python/tmp/cnn-tumor-area.png}
 		\caption{Tumor}
@@
 		\centering
-		\includegraphics[scale=0.5]{python/bin/cnn-epilepsy.png}
+		\includegraphics[scale=0.5]{python/tmp/cnn-epilepsy.png}
 		\caption{Epilepsy}
@@
 	\begin{adjustbox}{width=\textwidth}
-		\input{python/bin/results.tex}
+		\input{python/tmp/results.tex}
 	\end{adjustbox}

### 2023-11-13 latex/ms.tex
.

@@
 \author{Paschalis Bizopoulos, George I. Lambrou and Dimitrios Koutsouris%
-\thanks{The authors are with Biomedical Engineering Laboratory, School of Electrical and Computer Engineering, National Technical University of Athens, Athens 15780, Greece e-mail: {\tt\small pbizopoulos@protonmail.com}, {\tt\small glamprou@med.uoa.gr}, {\tt\small dkoutsou@biomed.ntua.gr.}}
+\thanks{The authors are with Biomedical Engineering Laboratory, School of Electrical and Computer Engineering, National Technical University of Athens, Athens 15780, Greece e-mail: {\tt\small pbizop@gmail.com}, {\tt\small glamprou@med.uoa.gr}, {\tt\small dkoutsou@biomed.ntua.gr.}}
 }

### 2024-04-02 latex/python/main.py
convert to onnx

@@ -2,19 +2,15 @@ from __future__ import annotations
 
 from os import getenv
 from pathlib import Path
-from shutil import move, rmtree
 from typing import TypeVar
 
 import numpy as np
-import onnx
 import pandas as pd
 import requests
 import torch
 from matplotlib import pyplot as plt
-from onnx_tf.backend import prepare
 from PIL import Image
 from scipy.signal import spectrogram
-from tensorflowjs.converters import tf_saved_model_conversion_v2
 from torch import nn
 from torch.nn import functional
 from torch.optim import Adam
@@ -698,33 +694,6 @@ def resnet50(classes_num: int) -> nn.Module:
     return ResNet(Bottleneck, classes_num, expansion=4, layers=[3, 4, 6, 3])
 
 
-def save_tfjs_from_torch(
-    example_input: torch.Tensor,
-    model: nn.Module,
-    model_file_name: str,
-) -> None:
-    model_file_path = Path("tmp") / model_file_name
-    if model_file_path.exists():
-        rmtree(model_file_path)
-    model_file_path.mkdir()
-    torch.onnx.export(
-        model.cpu(),
-        example_input,
-        model_file_path / "model.onnx",
-        export_params=True,
-    )
-    model_onnx = onnx.load(model_file_path / "model.onnx")
-    model_tf = prepare(model_onnx)
-    model_tf.export_graph(model_file_path / "model")
-    tf_saved_model_conversion_v2.convert_tf_saved_model(
-        (model_file_path / "model").as_posix(),
-        model_file_path,
-        skip_op_check=True,
-    )
-    rmtree(model_file_path / "model")
-    (model_file_path / "model.onnx").unlink()
-
-
 def vgg11(classes_num: int) -> nn.Module:
     cfg = [64, "M", 128, "M", 256, 256, "M", 512, 512, "M", 512, 512, "M"]
     return VGG(classes_num, make_layers(cfg))
@@ -953,15 +922,13 @@ def main() -> None:  # noqa: C901, PLR0912, PLR0915
                 model_base_name_index,
             ] = accuracy_test
             if model_file_name == "resnet34-1D":
-                save_tfjs_from_torch(
-                    dataset_train[0][0].unsqueeze(0),
-                    model,
-                    model_file_name,
+                example_input = (dataset_train[0][0].unsqueeze(0),)
+                torch.onnx.export(
+                    model.cpu(),
+                    example_input,
+                    "tmp/model.onnx",
+                    export_params=True,
                 )
[…]

### 2025-10-16 packages/latex/ms.tex
init

--- 2023-11-13 latex/ms.tex
@@
 \IEEEoverridecommandlockouts{}
+
+\providecommand{\FILEPATH}{~/github.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/packages/python/tmp}
 
@@
   \begin{tikzpicture}[]
-		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{python/tmp/signal-epilepsy.png}};
+    \node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{\FILEPATH/signal-epilepsy.png}};
     \node[align=left] at (-4.2, 0) {$x_i$};
@@
     \draw[dashed,->] (-3.2, 0) -- (-3, 0);
-		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{python/tmp/cnn-epilepsy.png}};
+    \node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{\FILEPATH/cnn-epilepsy.png}};
     \draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
@@
   \centering
-	\rotatebox[origin=c]{90}{Original Signal}
+  \rotatebox[origin=l]{90}{\small Original Signal}
   \begin{subfigure}{0.19\linewidth}
     \centering
-		\includegraphics[scale=0.2]{python/tmp/signal-eyes-open.png}
+    \includegraphics[scale=0.2]{\FILEPATH/signal-eyes-open.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.2]{python/tmp/signal-eyes-closed.png}
+    \includegraphics[scale=0.2]{\FILEPATH/signal-eyes-closed.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.2]{python/tmp/signal-healthy-area.png}
+    \includegraphics[scale=0.2]{\FILEPATH/signal-healthy-area.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.2]{python/tmp/signal-tumor-area.png}
+    \includegraphics[scale=0.2]{\FILEPATH/signal-tumor-area.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.2]{python/tmp/signal-epilepsy.png}
+    \includegraphics[scale=0.2]{\FILEPATH/signal-epilepsy.png}
   \end{subfigure}
 
-	\rotatebox[origin=c]{90}{`Signal as Image'}
+  \rotatebox[origin=l]{90}{\small `Signal as Image'}
   \begin{subfigure}{0.19\linewidth}
     \centering
-		\includegraphics[scale=0.5]{python/tmp/signal-as-image-eyes-open.png}
+    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-eyes-open.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/signal-as-image-eyes-closed.png}
+    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-eyes-closed.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/signal-as-image-healthy-area.png}
+    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-healthy-area.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/signal-as-image-tumor-area.png}
+    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-tumor-area.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/signal-as-image-epilepsy.png}
+    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-epilepsy.png}
   \end{subfigure}
 
-	\rotatebox[origin=c]{90}{Spectrogram}
+  \rotatebox[origin=l]{90}{\small \hspace{1mm} Spectrogram}
   \begin{subfigure}{0.19\linewidth}
     \centering
-		\includegraphics[scale=0.5]{python/tmp/spectrogram-eyes-open.png}
+    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-eyes-open.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/spectrogram-eyes-closed.png}
+    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-eyes-closed.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/spectrogram-healthy-area.png}
+    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-healthy-area.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/spectrogram-tumor-area.png}
+    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-tumor-area.png}
   \end{subfigure}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/spectrogram-epilepsy.png}
+    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-epilepsy.png}
   \end{subfigure}
 
-	\rotatebox[origin=c]{90}{\hspace{5mm} one layer CNN}
+  \rotatebox[origin=l]{90}{\small \hspace{5mm} one layer CNN}
   \begin{subfigure}{0.19\linewidth}
     \centering
-		\includegraphics[scale=0.5]{python/tmp/cnn-eyes-open.png}
+    \includegraphics[scale=0.5]{\FILEPATH/cnn-eyes-open.png}
     \caption{Open}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/cnn-eyes-closed.png}
+    \includegraphics[scale=0.5]{\FILEPATH/cnn-eyes-closed.png}
     \caption{Closed}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/cnn-healthy-area.png}
+    \includegraphics[scale=0.5]{\FILEPATH/cnn-healthy-area.png}
     \caption{Healthy}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/cnn-tumor-area.png}
+    \includegraphics[scale=0.5]{\FILEPATH/cnn-tumor-area.png}
     \caption{Tumor}
@@
     \centering
-		\includegraphics[scale=0.5]{python/tmp/cnn-epilepsy.png}
+    \includegraphics[scale=0.5]{\FILEPATH/cnn-epilepsy.png}
     \caption{Epilepsy}
@@
   \begin{adjustbox}{width=\textwidth}
-		\input{python/tmp/results.tex}
+    \input{\FILEPATH/results.tex}
   \end{adjustbox}

### 2025-10-16 packages/html/script.js

@@ -1,0 +1,122 @@
+const canvasHeight = 256;
+const canvasWidth = 256;
+const classNameArray = ["Open", "Closed", "Healthy", "Tumor", "Epilepsy"];
+const inputDiv = document.getElementById("input-div");
+const inputFileName =
+  "https://raw.githubusercontent.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/main/shells/html/prm/eeg-classification-example-data.txt";
+const loadingDialog = document.getElementById("loading-dialog");
+const outputDiv = document.getElementById("output-div");
+const signalFileReader = new FileReader();
+const signalInputFile = document.getElementById("signal-input-file");
+
+let csvDataset;
+let csvDatasetMax;
+let csvDatasetMin;
+let line;
+let session;
+signalFileReader.onload = signalFileReaderOnLoad;
+signalInputFile.onchange = signalInputFileOnChange;
+
+function drawSignal(text) {
+  const array = text.match(/\d+(?:\.\d+)?/g).map(Number);
+  csvDataset = tf.tensor(array);
+  csvDatasetMax = csvDataset.max().arraySync();
+  csvDatasetMin = csvDataset.min().arraySync();
+  const x = d3
+    .scaleLinear()
+    .domain([0, csvDataset.size])
+    .range([0, canvasWidth]);
+  const y = d3
+    .scaleLinear()
+    .domain([csvDatasetMin, csvDatasetMax])
+    .range([canvasHeight, 0]);
+  line = d3
+    .line()
+    .x((d, i) => x(i))
+    .y((d) => y(d));
+  d3.select("#path-input").attr("d", line(csvDataset.arraySync()));
+}
+
+async function loadModel(predictFunction) {
+  loadingDialog.showModal();
+  session = await ort.InferenceSession.create("./prm/model.onnx");
+  loadingDialog.close();
+  predictFunction();
+}
+
+async function predictView() {
+  if (csvDataset === undefined) {
+    return;
+  }
+  if (session === undefined) {
+    return;
+  }
+  let csvDatasetTmp = csvDataset.expandDims(0).expandDims(2);
+  csvDatasetTmp = tf.image.resizeBilinear(csvDatasetTmp, [1, 178]);
+  csvDatasetTmp = csvDatasetTmp.reshape([1, 1, 178]);
+  const tensorA = new ort.Tensor(
+    "float32",
+    csvDatasetTmp.dataSync(),
+    [1, 1, 178],
+  );
[…]

### 2025-10-16 packages/python/main.py

@@ -1,0 +1,1058 @@
+#!/usr/bin/env python3
+"""Signal2Image Modules in Deep Neural Networks for EEG Classification."""
+from __future__ import annotations
+
+import os
+from pathlib import Path
+from typing import TypeVar
+
+import numpy as np
+import pandas as pd
+import PIL
+import torch
+from matplotlib import pyplot as plt
+from scipy.signal import spectrogram
+from torch import nn
+from torch.nn import functional
+from torch.optim import Adam
+from torch.utils.data import DataLoader, Dataset
+from torchvision import models
+
+_PACKAGE_PATH = (
+    Path.home()
+    / "github.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/packages/python/"  # noqa: E501
+)
+if Path(__file__).resolve().as_posix().startswith("/nix/store/"):
+    _PARENT_PATH = Path(__file__).resolve().parent
+else:
+    _PARENT_PATH = _PACKAGE_PATH
+_OUT_PATH = _PACKAGE_PATH / "tmp"
+_OUT_PATH.mkdir(exist_ok=True, parents=True)
+
+
+class _Alexnet(nn.Module):  # type: ignore[misc]
+    def __init__(self, num_classes: int) -> None:
+        super().__init__()
+        self.conv1 = nn.Conv1d(1, 64, kernel_size=11, stride=4, padding=2)
+        self.relu = nn.ReLU()
+        self.maxpool1d = nn.MaxPool1d(kernel_size=3, stride=2)
+        self.conv2 = nn.Conv1d(64, 192, kernel_size=5, padding=2)
+        self.conv3 = nn.Conv1d(192, 384, kernel_size=3, padding=1)
+        self.conv4 = nn.Conv1d(384, 256, kernel_size=3, padding=1)
+        self.conv5 = nn.Conv1d(256, 256, kernel_size=3, padding=1)
+        self.dropout = nn.Dropout()
+        self.linear1 = nn.Linear(256 * 4, 4096)
+        self.linear2 = nn.Linear(4096, 4096)
+        self.linear3 = nn.Linear(4096, num_classes)
+
+    def forward(self, signal: torch.Tensor) -> torch.Tensor:
+        out = self.conv1(signal)
+        out = self.relu(out)
+        out = self.maxpool1d(out)
+        out = self.conv2(out)
+        out = self.relu(out)
+        out = self.maxpool1d(out)
+        out = self.conv3(out)
[…]

### 2025-10-16 packages/python/main.py
.

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 """Signal2Image Modules in Deep Neural Networks for EEG Classification."""
+
 from __future__ import annotations
 
 import os

### 2025-10-21 packages/default/main.py
.

@@ -21,7 +21,7 @@ from torchvision import models
 
 _PACKAGE_PATH = (
     Path.home()
-    / "github.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/packages/python/"  # noqa: E501
+    / "github.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/packages/default/"  # noqa: E501
 )
 if Path(__file__).resolve().as_posix().startswith("/nix/store/"):
     _PARENT_PATH = Path(__file__).resolve().parent

### 2025-10-21 packages/default/main.py
.

@@ -19,16 +19,12 @@ from torch.optim import Adam
 from torch.utils.data import DataLoader, Dataset
 from torchvision import models
 
-_PACKAGE_PATH = (
+_OUT_PATH = (
     Path.home()
-    / "github.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/packages/default/"  # noqa: E501
+    / "github.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/packages/default/tmp/"  # noqa: E501
 )
-if Path(__file__).resolve().as_posix().startswith("/nix/store/"):
-    _PARENT_PATH = Path(__file__).resolve().parent
-else:
-    _PARENT_PATH = _PACKAGE_PATH
-_OUT_PATH = _PACKAGE_PATH / "tmp"
 _OUT_PATH.mkdir(exist_ok=True, parents=True)
+_PARENT_PATH = Path(__file__).resolve().parent
 
 
 class _Alexnet(nn.Module):  # type: ignore[misc]
